---
title: "R Notebook"
output: html_notebook
---

I am lifting this code from Georgios Karamanis' [repo](https://github.com/gkaramanis/aRtist/blob/main/genuary/2022/2022-28/2022-28.R)

Load packages:
```{r load-packages, warning=FALSE, message=FALSE}
library(magick)
library(MexBrewer)
library(tidyverse)
library(truchet)
```

## Process image

Read the image using `magick::image_read()`:
```{r}
#me <- image_read("me_lg.jpg")
me <- image_read("selfie.jpg")
```

Check the size of the image: 
```{r}
image_info(me)
```

Scale image:
```{r}
me_scaled <- me %>% 
  image_scale("500")
```

Change the colorspace to gray:
```{r}
me_scaled <- me_scaled %>% 
  image_convert(colorspace = "gray")
```

This is the image after changing to grayscale:
```{r}
magick::image_ggplot(me_scaled)
```

Create array and number rows and columns:
```{r}
img_array <- drop(as.integer(me_scaled[[1]]))
rownames(img_array) <- 1:nrow(img_array)
colnames(img_array) <- ncol(img_array):1
```

Create data frame from array and rename columns
```{r}
img_df <- as.data.frame.table(img_array) %>% 
  `colnames<-`(c("y", "x", "b")) %>%
  mutate(x = as.numeric(x),
         y = - (as.numeric(y) - image_info(me_scaled)$height))
```

Sample from the image:
```{r}
img_df <- img_df %>% filter(log(b) < 4.5)
```

```{r}
img_df <- img_df %>%
  mutate(scale_p = case_when(log(b) <= 4.0 ~ 1/2,
                             log(b) >  4.0 ~ 1))
```



Create tiles:
```{r}
tiles_1 <- st_truchet_p(type = "-")
tiles_2 <- st_truchet_p(type = "-", scale_p = 1/2)
```

Assemble mosaic:
```{r}
df <- img_df
mosaic <- st_truchet_ms(t1 = tiles_1, t2 = tiles_2, df = df)
```

