---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Self-portrait

<!-- badges: start -->
<!-- badges: end -->

So I am making a self-portrait using the first few tens of thousands of digits of pi. 

I will use the following packages:
```{r load-packages, warning=FALSE, message=FALSE}
library(magick)
library(MexBrewer)
library(tidyverse)
```

## Process image

Read the image using `magick::image_read()`:
```{r}
#me <- image_read("me_lg.jpg")
me <- image_read("selfie.jpg")
```

Check the size of the image: 
```{r}
image_info(me)
```

Scale image:
```{r}
me_scaled <- me %>% 
  image_scale("500")
```

Change the colorspace to gray:
```{r}
me_scaled <- me_scaled %>% 
  image_convert(colorspace = "gray")
```

This is the image after changing to grayscale:
```{r}
magick::image_ggplot(me_scaled)
```

Create array and number rows and columns:
```{r}
img_array <- drop(as.integer(me_scaled[[1]]))
rownames(img_array) <- 1:nrow(img_array)
colnames(img_array) <- ncol(img_array):1
```

Create data frame from array and rename columns
```{r}
img_df <- as.data.frame.table(img_array) %>% 
  `colnames<-`(c("y", "x", "b")) %>%
  mutate(x = as.numeric(x),
         y = - (as.numeric(y) - image_info(me_scaled)$height))
```

Sample from the image:
```{r}
img_df <- img_df %>% filter(log(b) < 4.5)
```

Given the size, this means that I will use `r nrow(img_df)` digits of pi.

## Process text

Grabbed the first one million digits of pi from here: https://pi2e.ch/blog/2017/03/10/pi-digits-download/#download

```{r}
text1.v <- scan("pi.txt", what="character", sep="\n")
```

Join all the lines into one long string and convert to lower case:
```{r}
text1.v <- text1.v %>%
  paste(collapse = " ")
```

Extract the number of digits needed for the image:
```{r}
pi.fragment <- text1.v %>%
  str_sub(1, nrow(img_df))
```

Create data frame with text:
```{r}
text_df <- data.frame(img_df %>% 
                        group_by(x) %>% 
                        arrange(desc(y)),
            text = pi.fragment %>%
  str_extract_all(boundary("character")) %>% 
  unlist())

```

## Put together

Plot image with text:
```{r}
col_palette <- mex.brewer("Tierra")

ggplot(text_df) +
  geom_text(aes(x = x, 
                y = y, 
                color = -b, 
                label = text,
                size = -b)) +
  coord_equal() + 
  scale_color_gradientn(colors = col_palette) +
  scale_size(range = c(0.75, 1.55)) +
  theme_void() +
  theme(legend.position = "none")

ggsave("me-pi-tierra.png", 
       width = 7,
       units = "in")
```
