---
title: "Experiments with Fidenza"
output: html_notebook
---

My basic code implementing the Fidenza algorithm is in the README.Rmd file in `04-fidenza`.

Here I want to play with it a bit more.

For example, I used the length of the path but could use the sequence of steps to modify some aesthetic.

I will use the following packages:
```{r load-packages, cache = FALSE, warning=FALSE, message=FALSE}
library(ggforce)
library(MexBrewer)
library(tidyverse)
```

This are the basic steps:

1. Generate a grid
- Important parameters: size of the grid and valence of the coordinates (positive/negative)

2. Generate a flow field on the grid
- Important parameters: offset and formulas for the angles of the flow field

3. Generate paths
- Important parameters: resolution, number of iterations (length of path), number of paths 

## Generate Grid

```{r}
# Size of grid
n_min <- -17 
n_max <- 18
# Length of segment
l <- sqrt(2) + 0.1

df <- data.frame(expand.grid(x = seq(n_min, n_max, 1), y = seq(n_min, n_max, 1)))
```

Create and plot the flow field:
```{r}
# Offsets
x_o <- -0
y_o <- -0

df <- df %>%
  mutate(angle = ((x - x_o) * (y - y_o)) /(n_max - n_min)^2 * 2 * pi,
         xend = (x + l * cos(angle)),
         yend = (y + l * sin(angle)))

df %>%
  ggplot() +
  geom_segment(aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend)) +
  geom_point(aes(x = xend, 
                 y =yend)) +
  coord_equal() +
  theme_void()
```

Another possible parameter is using the valence of the coordinates to alter the angle:
```{r}
# Offsets
x_o <- -0
y_o <- -0

df <- df %>%
  mutate(angle = ((x - x_o) * (y - y_o)) /(n_max - n_min)^2 * 2 * pi * sign(x * y), # add the signs
         xend = (x + l * cos(angle)),
         yend = (y + l * sin(angle)))

df %>%
  ggplot() +
  geom_segment(aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend)) +
  geom_point(aes(x = xend, 
                 y =yend)) +
  coord_equal() +
  theme_void()
```

The valence could be used to change the direction of the displacement of the coordinate, instead of the angle:
```{r}
# Offsets
x_o <- -0
y_o <- -0

df <- df %>%
  mutate(angle = ((x - x_o) * (y - y_o)) /(n_max - n_min)^2 * 2 * pi, # add the signs
         xend = (x + sign(x) * l * cos(angle)),
         yend = (y + sign(y) * l * sin(angle)))

df %>%
  ggplot() +
  geom_segment(aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend)) +
  geom_point(aes(x = xend, 
                 y =yend)) +
  coord_equal() +
  theme_void()
```

Another possible parameter is an initial rotation:
```{r}
# Offsets
x_o <- -0
y_o <- -0
init_r <- 1/8

df <- df %>%
  mutate(angle = ((x - x_o) * (y - y_o)) /(n_max - n_min)^2 * 2 * pi + init_r * pi, # add the signs
         xend = (x + l * cos(angle)),
         yend = (y + l * sin(angle)))

df %>%
  ggplot() +
  geom_segment(aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend)) +
  geom_point(aes(x = xend, 
                 y =yend)) +
  coord_equal() +
  theme_void()
```

This one has an initial rotation and valence for the angle:
```{r}
# Offsets
x_o <- -0
y_o <- -0
init_r <- 1/8

df <- df %>%
  mutate(angle = (((x - x_o) * (y - y_o)) /(n_max - n_min)^2 * 2 * pi + init_r * pi) * sign(x * y), # add the signs
         xend = (x + l * cos(angle)),
         yend = (y + l * sin(angle)))

df %>%
  ggplot() +
  geom_segment(aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend)) +
  geom_point(aes(x = xend, 
                 y =yend)) +
  coord_equal() +
  theme_void()
```

This one has an initial rotation and valence for the displacement:
```{r}
# Offsets
x_o <- -0
y_o <- -0
init_r <- 1/8

df <- df %>%
  mutate(angle = ((x - x_o) * (y - y_o)) /(n_max - n_min)^2 * 2 * pi + init_r * pi, # add the signs
         xend = (x + sign(x) * l * cos(angle)),
         yend = (y + sign(y) * l * sin(angle)))

df %>%
  ggplot() +
  geom_segment(aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend)) +
  geom_point(aes(x = xend, 
                 y =yend)) +
  coord_equal() +
  theme_void()
```

This one has an initial rotation, valence for the displacement _and_ valence for the angle:
```{r}
# Offsets
x_o <- -0
y_o <- -0
init_r <- 1/8

df <- df %>%
  mutate(angle = (((x - x_o) * (y - y_o)) /(n_max - n_min)^2 * 2 * pi + init_r * pi) * sign(x * y), # add the signs
         xend = (x + sign(x) * l * cos(angle)),
         yend = (y + sign(y) * l * sin(angle)))

df %>%
  ggplot() +
  geom_segment(aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend)) +
  geom_point(aes(x = xend, 
                 y =yend)) +
  coord_equal() +
  theme_void()
```

Make paths using the last flow field:
```{r}
# Set seed for reproducibility
#set.seed(346363)

# Parameters for creating the paths
res <- 0.2 # Resolution for the path, smaller numbers create more points per path/smoother paths
n_iter <- 20 # Number of iterations per path
n_path <- 500 # Number of paths

# Sample starting points
st_point <- data.frame(x = runif(n_path, n_min, n_max),
                       #x = 2,
                       y = runif(n_path, n_min, n_max))

# Initialize data frame with paths
paths <- data.frame(x = numeric(), y = numeric(), step = numeric(), path = numeric())

for(p in 1:n_path){
  paths <- rbind(paths,
                 data.frame(st_point[p,], step = 1, path = p))
  next_x <- st_point[p, "x"]
  next_y <- st_point[p, "y"]
  for(i in 1:n_iter){
    # With the next point, retrieve the angle of the closest point in the direction of the flow
    angle <- df %>% 
      mutate(d = sqrt((x - next_x)^2 + (y - next_y)^2)) %>%
      filter(d == min(d)) %>%
      pull(angle)
    # Calculate the coordinates of the new next point and bind to paths
    paths <- rbind(paths,
                   data.frame(x = next_x + sign(next_x) * res * cos(angle), # Important to multiply by the sign of the next point
                              y = next_y + sign(next_y) * res * sin(angle), # Important to multiply by the sign of the next point
                              step = i + 1,
                              path = p))
    # Find the next starting point for the search
    next_x <- slice_tail(paths) %>%
      pull(x)
    next_y <- slice_tail(paths) %>%
      pull(y)
    
    # Check the boundary condition
    boundary_condition <- next_x < n_min | next_x >= n_max |
      next_y < n_min | next_y >= n_max
    # If at the boundary set i to n_iter to complete the loop
    if (boundary_condition) break
  }
}

# Rename paths

paths_ex3 <- paths
```

Plot paths:
```{r paths-ex3}
ggplot() + 
  geom_line(data = paths_ex3,
            aes(x = x,
                y = y,
                group = path),
            color = "blue",
            size = 1) +
  geom_segment(data = df,
               aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend)) +
  geom_point(data = df,
             aes(x = xend, 
                 y =yend)) +
  coord_equal() +
  theme_void() + 
  theme(legend.position = "none")
```

Instead of lines use symbols:
```{r}
ggplot() + 
  geom_point(data = paths_ex3 %>%
               mutate(p_grid = (x * y)^2),
             aes(x = x,
                 y = y,
                 group = path, 
                 color =p_grid),
             size = 1) +
  coord_equal() +
  theme_void() + 
  theme(legend.position = "none")
```

Add length of path to table:
```{r}
paths_ex3 <- paths_ex3 %>% 
  left_join(paths_ex3 %>%
              group_by(path) %>%
              summarize(l_path = n(), # length of path
                        .groups = "drop"),
            by = "path") 
```

Change the size of the symbols based on their position in the path:
```{r}
paths_ex3 <- paths_ex3 %>%
  mutate(p_grid = (x * y)^2,
         size = 1 / (abs(step - l_path/2) + 1))

ggplot(data = paths_ex3) + 
  geom_circle(aes(x0 = x,
                  y0 = y, 
                  fill =p_grid,
                  color = p_grid,
                  r = size * res),
              size = 1) +
  geom_point(aes(x = x - 0.7 * size * res * pi/4,
                 y = y + 0.7 * size * res * pi/4),
             color = "white", 
             size = 0.1) +
  coord_equal() +
  theme_void() + 
  theme(legend.position = "none")
```

Make pretty with palette `Ronda`:
```{r}
col_palette <- mex.brewer("Ronda")

paths_ex3 <- paths_ex3 %>%
  mutate(p_grid = (x * y)^2,
         size = 1 / (abs(step - l_path/2) + 1))

ggplot() + 
  geom_rect(aes(xmin = n_min, 
                xmax = n_max, 
                ymin = n_min, 
                ymax = n_max),
            fill = "black") +
  geom_circle(data = paths_ex3,
              aes(x0 = x,
                  y0 = y,
                  fill =p_grid,
                  color = p_grid,
                  r = 1.2 * size * res)) +
  geom_point(data = paths_ex3,
             aes(x = x - 1.2 * size * res * pi/4,
                 y = y + 1.2 * size * res * pi/4),
             color = col_palette[4],
             size = 0.1) +
  geom_circle(aes(x0 = 0,
                  y0 = 0,
                  r = 4),
              color = col_palette[4],
              fill = "black",
              size = 2) +
  geom_rect(aes(xmin = n_min, 
                xmax = n_max, 
                ymin = n_min, 
                ymax = n_max),
            fill = NA,
            color = col_palette[10]) +
  scale_color_gradientn(colors = col_palette) +
  coord_equal() +
  theme_void() + 
  theme(legend.position = "none")
```

Make pretty with palette `Revolucion`. The color depends on the position in the grid:
```{r}
col_palette <- mex.brewer("Revolucion")

paths_ex3 <- paths_ex3 %>%
  mutate(p_grid = (x * y)^2,
         size = 1 / (abs(step - l_path/2) + 1))

ggplot() + 
  geom_rect(aes(xmin = n_min, 
                xmax = n_max, 
                ymin = n_min, 
                ymax = n_max),
            fill = "black") +
  geom_circle(data = paths_ex3,
              aes(x0 = x,
                  y0 = y,
                  fill =p_grid,
                  color = p_grid,
                  r = 1.2 * size * res)) +
  geom_point(data = paths_ex3,
             aes(x = x - 1.2 * size * res * pi/4,
                 y = y + 1.2 * size * res * pi/4),
             color = col_palette[4],
             size = 0.1) +
  geom_circle(aes(x0 = 0,
                  y0 = 0,
                  r = 4),
              color = col_palette[4],
              fill = "black",
              size = 2) +
  geom_rect(aes(xmin = n_min, 
                xmax = n_max, 
                ymin = n_min, 
                ymax = n_max),
            fill = NA,
            color = col_palette[10]) +
  scale_color_gradientn(colors = col_palette) +
  coord_equal() +
  theme_void() + 
  theme(legend.position = "none")
```

Make pretty with palette `Revolucion` but now change the rate of change of the colors:
```{r}
col_palette <- mex.brewer("Revolucion")

paths_ex3 <- paths_ex3 %>%
  mutate(p_grid = (x * y)^2,
         size = 1 / (abs(step - l_path/2) + 1))

ggplot() + 
  geom_rect(aes(xmin = n_min, 
                xmax = n_max, 
                ymin = n_min, 
                ymax = n_max),
            fill = "black") +
  geom_circle(data = paths_ex3,
              aes(x0 = x,
                  y0 = y,
                  fill = p_grid^(1/3),
                  color = p_grid^(1/3),
                  r = 1.2 * size * res)) +
  geom_point(data = paths_ex3,
             aes(x = x - 1.2 * size * res * pi/4,
                 y = y + 1.2 * size * res * pi/4),
             color = col_palette[4],
             size = 0.1) +
  geom_segment(aes(x = n_min, xend = n_max, y = 0, yend = 0),
             color = col_palette[4],
             size = 3) +
  geom_segment(aes(x = 0, xend = 0, y = n_min, yend = n_max),
             color = col_palette[4],
             size = 3) +
  geom_circle(aes(x0 = 0,
                  y0 = 0,
                  r = 4),
              color = col_palette[4],
              fill = "black",
              size = 3) +
  geom_rect(aes(xmin = n_min, 
                xmax = n_max, 
                ymin = n_min, 
                ymax = n_max),
            fill = NA,
            color = col_palette[4], 
            size = 3) +
  scale_color_gradientn(colors = col_palette) +
  coord_equal() +
  theme_void() + 
  theme(legend.position = "none")

```

Make pretty with palette `Revolucion` but now the colors depend on the position on the path:
```{r}
col_palette <- mex.brewer("Revolucion")

paths_ex3 <- paths_ex3 %>%
  mutate(p_grid = (x * y)^2,
         size = 1 / (abs(step - l_path/2) + 1))

ggplot() + 
  geom_rect(aes(xmin = n_min, 
                xmax = n_max, 
                ymin = n_min, 
                ymax = n_max),
            fill = "black") +
  geom_circle(data = paths_ex3,
              aes(x0 = x,
                  y0 = y,
                  fill = step - l_path/2,
                  color = step - l_path/2,
                  r = 1.2 * size * res)) +
  geom_point(data = paths_ex3,
             aes(x = x - 1.2 * size * res * pi/4,
                 y = y + 1.2 * size * res * pi/4),
             color = col_palette[4],
             size = 0.1) +
  geom_circle(aes(x0 = 0,
                  y0 = 0,
                  r = 4),
              color = col_palette[4],
              fill = "black",
              size = 2) +
  geom_rect(aes(xmin = n_min, 
                xmax = n_max, 
                ymin = n_min, 
                ymax = n_max),
            fill = NA,
            color = col_palette[10]) +
  scale_color_gradientn(colors = col_palette) +
  coord_equal() +
  theme_void() + 
  theme(legend.position = "none")
```

Change the resolution:
```{r}
# Set seed for reproducibility
#set.seed(346363)

# Parameters for creating the paths
res <- 3 # Resolution for the path, smaller numbers create more points per path/smoother paths
n_iter <- 20 # Number of iterations per path
n_path <- 5000 # Number of paths

# Sample starting points
st_point <- data.frame(x = runif(n_path, n_min, n_max),
                       #x = 2,
                       y = runif(n_path, n_min, n_max))

# Initialize data frame with paths
paths <- data.frame(x = numeric(), y = numeric(), step = numeric(), path = numeric())

for(p in 1:n_path){
  paths <- rbind(paths,
                 data.frame(st_point[p,], step = 1, path = p))
  next_x <- st_point[p, "x"]
  next_y <- st_point[p, "y"]
  for(i in 1:n_iter){
    # With the next point, retrieve the angle of the closest point in the direction of the flow
    angle <- df %>% 
      mutate(d = sqrt((x - next_x)^2 + (y - next_y)^2)) %>%
      filter(d == min(d)) %>%
      pull(angle)
    # Calculate the coordinates of the new next point and bind to paths
    paths <- rbind(paths,
                   data.frame(x = next_x + sign(next_x) * res * cos(angle), # Important to multiply by the sign of the next point
                              y = next_y + sign(next_y) * res * sin(angle), # Important to multiply by the sign of the next point
                              step = i + 1,
                              path = p))
    # Find the next starting point for the search
    next_x <- slice_tail(paths) %>%
      pull(x)
    next_y <- slice_tail(paths) %>%
      pull(y)
    
    # Check the boundary condition
    boundary_condition <- next_x < n_min | next_x >= n_max |
      next_y < n_min | next_y >= n_max
    # If at the boundary set i to n_iter to complete the loop
    if (boundary_condition) break
  }
}

# Rename paths

paths_ex4 <- paths
```

Plot paths:
```{r paths-ex4}
# Add length of path to table:
paths_ex4 <- paths_ex4 %>% 
  left_join(paths_ex4 %>%
              group_by(path) %>%
              summarize(l_path = n(), # length of path
                        .groups = "drop"),
            by = "path") 

ggplot() + 
  geom_line(data = paths_ex4,
            aes(x = x,
                y = y,
                group = path,
                color = step - l_path/2),
            size = 0.1) +
  geom_segment(data = df,
               aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend)) +
  geom_point(data = df,
             aes(x = xend, 
                 y =yend)) +
  coord_equal() +
  theme_void() + 
  theme(legend.position = "none")
```

```{r}
col_palette <- mex.brewer("Revolucion")

paths_ex4 <- paths_ex4 %>%
  mutate(p_grid = (x * y)^2,
         size = 1 / (abs(step - l_path/2) + 1))

ggplot() + 
  geom_rect(aes(xmin = n_min, 
                xmax = n_max, 
                ymin = n_min, 
                ymax = n_max),
            fill = "black") +
  geom_line(data = paths_ex4 %>%
              filter(x > n_min & x < n_max, 
                     y > n_min & y < n_max),
              aes(x = x,
                  y = y,
                  group = path,
                  color = p_grid^(1/3))) +
  geom_segment(aes(x = n_min, xend = n_max, y = 0, yend = 0),
             color = col_palette[10],
             size = 3) +
  geom_segment(aes(x = 0, xend = 0, y = n_min, yend = n_max),
             color = col_palette[10],
             size = 3) +
  geom_circle(aes(x0 = 0,
                  y0 = 0,
                  r = 4),
              color = col_palette[10],
              fill = "black",
              size = 3) +
  geom_rect(aes(xmin = n_min, 
                xmax = n_max, 
                ymin = n_min, 
                ymax = n_max),
            fill = NA,
            color = col_palette[10], 
            size = 3) +
  scale_color_gradientn(colors = col_palette) +
  coord_equal() +
  theme_void() + 
  theme(legend.position = "none")
```



## Experiments with angle and resolutions


```{r}
# Size of grid
n_min <- -17 
n_max <- 18
# Length of segment
l <- sqrt(2) + 0.1

df <- data.frame(expand.grid(x = seq(n_min, n_max, 1), y = seq(n_min, n_max, 1)))
```


Create new flow field:
```{r}
# Offsets
x_o <- -15
y_o <- 5
init_r <- 0
d_angle <- 2

# remove the valence
df <- df %>%
  mutate(angle = (((x - x_o) * (y - y_o)) /(n_max - n_min)^2 * d_angle * pi + init_r * pi),# * sign(x * y), # add the signs
         xend = (x + l * cos(angle)),
         yend = (y + l * sin(angle)))

df %>%
  ggplot() +
  geom_segment(aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend)) +
  geom_point(aes(x = xend, 
                 y =yend)) +
  coord_equal() +
  theme_void()
```

Add obstacles:
```{r}
df <- df %>%
  mutate(r1 = sqrt((x - 8)^2 + (y - 8)^2),
         r2 = sqrt((x + 8)^2 + (y + 8)^2)) %>%
  filter(r1 > 4,
         r2 > 4)

df %>%
  ggplot() +
  geom_segment(aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend)) +
  geom_point(aes(x = xend, 
                 y =yend)) +
  coord_equal() +
  theme_void()

```

Change the resolution:
```{r}
# Set seed for reproducibility
#set.seed(346363)

# Parameters for creating the paths
res <- 3 # Resolution for the path, smaller numbers create more points per path/smoother paths
n_iter <- 50 # Number of iterations per path
n_path <- 5000 # Number of paths

# Sample starting points
st_point <- data.frame(x = runif(n_path, n_min, n_max),
                       #x = 2,
                       y = runif(n_path, n_min, n_max)) %>%
  mutate(r1 = sqrt((x - 8)^2 + (y - 8)^2),
         r2 = sqrt((x + 8)^2 + (y + 8)^2)) %>%
  filter(r1 > 4,
         r2 > 4) %>%
  select(-starts_with("r"))

# Update number of paths to account for the starting poins eliminated due to obstacles
n_path <- nrow(st_point)

# Initialize data frame with paths
paths <- data.frame(x = numeric(), y = numeric(), step = numeric(), path = numeric())

for(p in 1:n_path){
  paths <- rbind(paths,
                 data.frame(st_point[p,], step = 1, path = p))
  next_x <- st_point[p, "x"]
  next_y <- st_point[p, "y"]
  for(i in 1:n_iter){
    # With the next point, retrieve the angle of the closest point in the direction of the flow
    angle <- df %>% 
      mutate(d = sqrt((x - next_x)^2 + (y - next_y)^2)) %>%
      filter(d == min(d))
    min_d <- angle %>% pull(d)
    angle <- angle %>% pull(angle)
    # Calculate the coordinates of the new next point and bind to paths
    paths <- rbind(paths,
                   data.frame(x = next_x + res * cos(angle), # Removed the valence
                              y = next_y + res * sin(angle), # Removed the valence
                              step = i + 1,
                              path = p))
    # Find the next starting point for the search
    next_x <- slice_tail(paths) %>%
      pull(x)
    next_y <- slice_tail(paths) %>%
      pull(y)
    
    # Check the boundary condition
    boundary_condition <- next_x < n_min | next_x >= n_max |
      next_y < n_min | next_y >= n_max | min_d > sqrt(2) + 0.1
    # If at the boundary set i to n_iter to complete the loop
    if (boundary_condition) break
  }
}

# Rename paths

paths_ex5 <- paths
```

Plot paths:
```{r paths-ex5}
# Add length of path to table:
paths_ex5 <- paths_ex5 %>% 
  left_join(paths_ex5 %>%
              group_by(path) %>%
              summarize(l_path = n(), # length of path
                        .groups = "drop"),
            by = "path") 

ggplot() + 
  geom_path(data = paths_ex5,
            aes(x = x,
                y = y,
                group = path),
            color = "blue",
            size = 1) +
  geom_segment(data = df,
               aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend)) +
  geom_point(data = df,
             aes(x = xend, 
                 y =yend)) +
  coord_equal() +
  theme_void() + 
  theme(legend.position = "none")
```

Obstacle avoidance not working great, wonder why.

Prettify:
```{r}
col_palette <- mex.brewer("Revolucion")

paths_ex5 <- paths_ex5 %>%
  mutate(p_grid = ((x - n_min) * (y - n_min ))^2,
         size = 1 / (abs(step - l_path/2) + 1))

plot1 <- ggplot() + 
  geom_rect(aes(xmin = n_min, 
                xmax = n_max, 
                ymin = n_min, 
                ymax = n_max),
            fill = "black") +
  geom_path(data = paths_ex5 %>%
              filter(x > n_min & x < n_max,
                     y > n_min & y < n_max),
              aes(x = x,
                  y = y,
                  group = path,
                  color = p_grid^(1/3))) +
  geom_circle(aes(x0 = -8,
                  y0 = -8,
                  r = 4),
              color = col_palette[4],
              fill = col_palette[8],
              size = 3) +
   geom_circle(aes(x0 = 8,
                   y0 = 8,
                   r = 4),
               color = col_palette[4],
               fill = col_palette[1],
               size = 3) +
  geom_rect(aes(xmin = n_min, 
                xmax = n_max, 
                ymin = n_min, 
                ymax = n_max),
            fill = NA,
            color = col_palette[8], 
            size = 3) +
  scale_color_gradientn(colors = col_palette) +
  coord_equal() +
  theme_void() + 
  theme(legend.position = "none")

plot1
```

```{r}
col_palette <- mex.brewer("Atentado")

paths_ex5 <- paths_ex5 %>%
  mutate(p_grid = ((x - n_min) * (y - n_min ))^2,
         size = 1 / (abs(step - l_path/2) + 1))

plot2 <- ggplot() + 
  geom_rect(aes(xmin = -n_min, 
                xmax = -n_max, 
                ymin = n_min, 
                ymax = n_max),
            fill = "black") +
  geom_path(data = paths_ex5 %>%
              filter(x > n_min & x < n_max,
                     y > n_min & y < n_max),
              aes(x = -x,
                  y = y,
                  group = path,
                  color = p_grid^(1/3))) +
  geom_circle(aes(x0 = 8,
                  y0 = -8,
                  r = 4),
              color = col_palette[4],
              fill = col_palette[8],
              size = 3) +
   geom_circle(aes(x0 = -8,
                   y0 = 8,
                   r = 4),
               color = col_palette[4],
               fill = col_palette[1],
               size = 3) +
  geom_rect(aes(xmin = -n_min, 
                xmax = -n_max, 
                ymin = n_min, 
                ymax = n_max),
            fill = NA,
            color = col_palette[8], 
            size = 3) +
  scale_color_gradientn(colors = col_palette) +
  coord_equal() +
  theme_void() + 
  theme(legend.position = "none")

plot2
```

```{r}
col_palette <- mex.brewer("Alacena")

paths_ex5 <- paths_ex5 %>%
  mutate(p_grid = ((x - n_min) * (y - n_min ))^2,
         size = 1 / (abs(step - l_path/2) + 1))

plot3 <- ggplot() + 
  geom_rect(aes(xmin = n_min, 
                xmax = n_max, 
                ymin = -n_min, 
                ymax = -n_max),
            fill = "black") +
  geom_path(data = paths_ex5 %>%
              filter(x > n_min & x < n_max,
                     y > n_min & y < n_max),
              aes(x = x,
                  y = -y,
                  group = path,
                  color = p_grid^(1/3))) +
  geom_circle(aes(x0 = 8,
                  y0 = -8,
                  r = 4),
              color = col_palette[4],
              fill = col_palette[8],
              size = 3) +
   geom_circle(aes(x0 = -8,
                   y0 = 8,
                   r = 4),
               color = col_palette[4],
               fill = col_palette[1],
               size = 3) +
  geom_rect(aes(xmin = n_min, 
                xmax = n_max, 
                ymin = -n_min, 
                ymax = -n_max),
            fill = NA,
            color = col_palette[8], 
            size = 3) +
  scale_color_gradientn(colors = col_palette) +
  coord_equal() +
  theme_void() + 
  theme(legend.position = "none")

plot3
```


```{r}
col_palette <- mex.brewer("Ronda")

paths_ex5 <- paths_ex5 %>%
  mutate(p_grid = ((x - n_min) * (y - n_min ))^2,
         size = 1 / (abs(step - l_path/2) + 1))

plot4 <- ggplot() + 
  geom_rect(aes(xmin = -n_min, 
                xmax = -n_max, 
                ymin = -n_min, 
                ymax = -n_max),
            fill = "black") +
  geom_path(data = paths_ex5 %>%
              filter(x > n_min & x < n_max,
                     y > n_min & y < n_max),
              aes(x = -x,
                  y = -y,
                  group = path,
                  color = p_grid^(1/3))) +
  geom_circle(aes(x0 = -8,
                  y0 = -8,
                  r = 4),
              color = col_palette[4],
              fill = col_palette[8],
              size = 3) +
   geom_circle(aes(x0 = 8,
                   y0 = 8,
                   r = 4),
               color = col_palette[4],
               fill = col_palette[1],
               size = 3) +
  geom_rect(aes(xmin = -n_min, 
                xmax = -n_max, 
                ymin = -n_min, 
                ymax = -n_max),
            fill = NA,
            color = col_palette[8], 
            size = 3) +
  scale_color_gradientn(colors = col_palette) +
  coord_equal() +
  theme_void() + 
  theme(legend.position = "none")

plot4
```

```{r fig.height=10}
library(patchwork)

(plot1 + plot2) / (plot3 + plot4)
```

