---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Isometric Perspective

<!-- badges: start -->
<!-- badges: end -->

This will be a quick experiment with isometric perspective.

I use these package:
```{r setup}
library(MexBrewer)
library(purrr)
library(sf)
library(showtext)
library(tidyverse)
```

Create a function to generate the faces of an isometric cube "up" direction:
```{r}
cube_up <- function(x, y){
  face_1 <- matrix(c(x, y, 
                     x-sqrt(3)/2, y + 1/2,
                     x -sqrt(3)/2, y + 1 + 1/2,
                     x, y + 1,
                     x, y),
                   ncol = 2,
                   byrow = TRUE)
  
  # Convert coordinates to polygons and then to simple features
  face_1 <- data.frame(id = "left",
                       geometry = st_polygon(list(face_1)) %>% 
                         st_sfc()) %>% 
    st_as_sf()
  
  # Face 2
  face_2 <- matrix(c(x, y,
                     x, y + 1,
                     x + sqrt(3)/2, y + 1 + 1/2,
                     x + sqrt(3)/2, y + 1/2,
                     x, y),
                   ncol = 2,
                   byrow = TRUE)
  
  # Convert coordinates to polygons and then to simple features
  face_2 <- data.frame(id = "right",
                       geometry = st_polygon(list(face_2)) %>% 
                         st_sfc()) %>% 
    st_as_sf()
  
  # Face 3
  face_3 <- matrix(c(x, y + 1,
                     x - sqrt(3)/2, y + 1 + 1/2,
                     x, y + 2,
                     x + sqrt(3)/2, y + 1 + 1/2,
                     x, y + 1),
                   ncol = 2,
                   byrow = TRUE)
  
  # Convert coordinates to polygons and then to simple features
  face_3 <- data.frame(id = "top",
                       geometry = st_polygon(list(face_3)) %>% 
                         st_sfc()) %>% 
    st_as_sf()
  
  rbind(face_1,
        face_2,
        face_3)
}



```

Create a function to generate the faces of an isometric cube "down" direction:
```{r}
cube_down <- function(x, y){
  
  face_1 <- matrix(c(x, y + 1, 
                     x - sqrt(3)/2, y + 1/2,
                     x - sqrt(3)/2, y + 1 + 1/2,
                     x, y + 2,
                     x, y + 1),
                   ncol = 2,
                   byrow = TRUE)
  
  # Convert coordinates to polygons and then to simple features
  face_1 <- data.frame(id = "left",
                       geometry = st_polygon(list(face_1)) %>% 
                         st_sfc()) %>% 
    st_as_sf()
  
  # Face 2
  face_2 <- matrix(c(x, y + 1,
                     x, y + 2,
                     x + sqrt(3)/2, y + 1 + 1/2,
                     x + sqrt(3)/2, y + 1/2,
                     x, y + 1),
                   ncol = 2,
                   byrow = TRUE)
  
  # Convert coordinates to polygons and then to simple features
  face_2 <- data.frame(id = "right",
                       geometry = st_polygon(list(face_2)) %>% 
                         st_sfc()) %>% 
    st_as_sf()
  
  # Face 3
  face_3 <- matrix(c(x, y,
                     x - sqrt(3)/2, y + 1/2,
                     x, y + 1,
                     x+ sqrt(3)/2, y + 1/2,
                     x, y),
                   ncol = 2,
                   byrow = TRUE)
  
  # Convert coordinates to polygons and then to simple features
  face_3 <- data.frame(id = "bottom",
                       geometry = st_polygon(list(face_3)) %>% 
                         st_sfc()) %>% 
    st_as_sf()
  
  rbind(face_1,
        face_2,
        face_3)
}



```

Test functions:
```{r}
ggplot() +
  geom_sf(data = cube_down(2, 2),
          aes(fill = id))
```

Simple example assembling tiles:
```{r}
x_c <- c(1, 3)
y_c <- c(1, 2)

map2_dfr(.x = x_c, .y = y_c, ~cube_up(.x, .y)) %>% 
  ggplot() +
  geom_sf(aes(fill = id))
```

Create a mosaic - note the use of {purrr} functions:
```{r}
coords <-  expand.grid(x = seq(0, 10 * sqrt(3), sqrt(3)),
                       y = seq(0, 10, 2))

x_c <- coords$x
y_c <- coords$y

map2_dfr(.x = x_c, .y = y_c, ~cube_up(.x, .y)) %>% 
  ggplot() +
  geom_sf(aes(fill = id))
```

The coordinates of the tiles are not quite what I wanted. Recreate mosaic:
```{r}
coords <-  expand.grid(x = seq(0, 10 * sqrt(3), sqrt(3)),
                       y = seq(0, 10, 3)) %>%
  rbind(expand.grid(x = seq(sqrt(3)/2, 10 * sqrt(3), sqrt(3)),
                    y = seq(1 + 1/2, 10, 3))) %>%
  filter(sqrt((x - 5 * sqrt(3))^2 + (y - 5)^2) <= 4.5)

x_c <- coords$x
y_c <- coords$y

mosaic <- map2_dfr(.x = x_c, .y = y_c, ~cube_up(.x, .y)) 

mosaic %>% 
  ggplot() +
  geom_sf(aes(fill = id),
          color = "white")
```
Create a function to make lines:
```{r}
make_lines <- function(xmin, xmax, ymin, ymax){
  pts <- matrix(c(xmin, 
                  xmax, 
                  ymin, 
                  ymax), 
                ncol = 2, 
                byrow = FALSE)
    st_sf(st_geometry(st_linestring(pts)))
}
```

Make vertical lines:
```{r}
line_space <- 0.15

x_min <- seq(-5, 15 * sqrt(3), line_space - 0.05)
y_min <- rep(0, length(x_min))
y_max <- rep(15 * sqrt(3), length(x_min))

lines_v <- pmap_dfr(list(x_min, x_min, y_min, y_max), make_lines)

lines_v %>% 
  ggplot() +
  geom_sf(color = "black")
```

Make horizontal lines:
```{r}
y_min <- seq(-5, 15 * sqrt(3), line_space - 0.05)
x_min <- rep(0, length(y_min))
x_max <- rep(15 * sqrt(3), length(x_min))

lines_h <- pmap_dfr(list(x_min, x_max, y_min, y_min), make_lines)

lines_h %>% 
  ggplot() +
  geom_sf(color = "black")
```

Make diagonal lines (\\):
```{r}
height <- 10 * sqrt(3)
x_min <- seq(-15, 25 * sqrt(3), line_space)
y_max <- rep(height, length(x_min))
x_max <- x_min - height * sqrt(3)
y_min <- rep(0, length(x_min))


lines_dl <- pmap_dfr(list(x_min, x_max, y_min, y_max), make_lines)

lines_dl %>% 
  ggplot() +
  geom_sf(color = "black")
```

Make diagonal lines (/):
```{r}
height <- 10 * sqrt(3)
x_min <- seq(-25, 25 * sqrt(3), line_space)
y_max <- rep(height, length(x_min))
x_max <- x_min + height * sqrt(3)
y_min <- rep(0, length(x_min))


lines_dr <- pmap_dfr(list(x_min, x_max, y_min, y_max), make_lines)

lines_dr %>% 
  ggplot() +
  geom_sf(color = "black")
```

Intersect the lines with faces of the polygons:
```{r}
lines_v_intersect <- lines_v %>%
  st_intersection(mosaic %>%
                    filter(id == "right"))

lines_dr_intersect <- lines_dr %>%
  st_intersection(mosaic %>%
                    filter(id == "left"))

lines_dl_intersect <- lines_dl %>%
  st_intersection(mosaic %>%
                    filter(id == "top"))

lines_intersect <- rbind(lines_v_intersect,
                         lines_dr_intersect,
                         lines_dl_intersect)

ggplot() +
  geom_sf(data = lines_intersect,
          aes(color = id))
```

Add fonts:
```{r}
font_add_google("Monoton", "monoton")
font_add_google("Unica One", "unica")
showtext_auto()
```

Make pretty:
```{r}
ggplot() +
  geom_sf(data = lines_intersect %>%
            filter(id != "left"),
          color = "white",
          size = 0.5) +
  labs(title = "Isometric Perspective", caption = "@paezha") +
  theme_void() +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "black"),
        plot.title = element_text(
      size = rel(5), margin = margin(0, 0, 5, 0, unit = "pt"),
      family = "monoton", face = "bold"),
    plot.subtitle = element_text(
      size = rel(8), margin = margin(0, 0, 10, 0, unit = "pt"),
      family = "unica"),
    plot.caption = element_text(
      size = rel(5), margin = margin(10, 0, 0, 0, unit = "pt"),
      family = "unica"))

ggsave("isometric-bw.png")
```

## A variation

Use the whole grid but with different line patterns in parts:
```{r}
coords <-  expand.grid(x = seq(0, 10 * sqrt(3), sqrt(3)),
                       y = seq(0, 11, 3)) %>%
  rbind(expand.grid(x = seq(sqrt(3)/2, 11 * sqrt(3), sqrt(3)),
                    y = seq(1 + 1/2, 11, 3)))

coords_1 <- coords %>%
  filter(sqrt((x - 5 * sqrt(3))^2 + (y - 5)^2) <= 4.3)

coords_2 <- coords %>%
  filter(sqrt((x - 5 * sqrt(3))^2 + (y - 5)^2) > 4.3)

x_c <- coords_1$x
y_c <- coords_1$y

mosaic_1 <- map2_dfr(.x = x_c, .y = y_c, ~cube_up(.x, .y)) 


x_c <- coords_2$x
y_c <- coords_2$y

mosaic_2 <- map2_dfr(.x = x_c, .y = y_c, ~cube_up(.x, .y)) 

mosaic_1 %>% 
  ggplot() +
  geom_sf(aes(fill = id),
          color = "white")

mosaic_2 %>% 
  ggplot() +
  geom_sf(aes(fill = id),
          color = "white")
```

Intersect the lines with faces of the polygons:
```{r}
# Mosaic 1
lines_v_intersect_1 <- lines_v %>%
  st_intersection(mosaic_1 %>%
                    filter(id == "right"))

lines_dr_intersect_1 <- lines_dr %>%
  st_intersection(mosaic_1 %>%
                    filter(id == "left"))

lines_dl_intersect_1 <- lines_dl %>%
  st_intersection(mosaic_1 %>%
                    filter(id == "top"))

lines_intersect_1 <- rbind(lines_v_intersect_1,
                         lines_dr_intersect_1,
                         lines_dl_intersect_1)

# Mosaic 2
lines_v_intersect_2 <- lines_v %>%
  st_intersection(mosaic_2 %>%
                    filter(id == "left"))

lines_dr_intersect_2 <- lines_dr %>%
  st_intersection(mosaic_2 %>%
                    filter(id == "top"))

lines_dl_intersect_2 <- lines_dl %>%
  st_intersection(mosaic_2 %>%
                    filter(id == "right"))

lines_intersect_2 <- rbind(lines_v_intersect_2,
                         lines_dr_intersect_2,
                         lines_dl_intersect_2)

ggplot() +
  geom_sf(data = lines_intersect_1,
          aes(color = id))

ggplot() +
  geom_sf(data = lines_intersect_2,
          aes(color = id))
```

Make pretty:
```{r}
ggplot() +
  # geom_sf(data = mosaic_1,
  #         fill = "black",
  #         color = "white") +
  # geom_sf(data = mosaic_2,
  #         fill = "black",
  #         color = "white") +
  geom_sf(data = lines_intersect_1 %>%
            filter(id != "left"),
          color = "white",
          size = 0.5) +
  geom_sf(data = lines_intersect_2 %>%
            filter(id != "right"),
          color = "white",
          size = 0.5) +
  labs(title = "Isometric Perspective", caption = "@paezha") +
  theme_void() +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "black"),
        plot.title = element_text(
      size = rel(5), margin = margin(0, 0, 5, 0, unit = "pt"),
      family = "monoton", face = "bold"),
    plot.subtitle = element_text(
      size = rel(8), margin = margin(0, 0, 10, 0, unit = "pt"),
      family = "unica"),
    plot.caption = element_text(
      size = rel(5), margin = margin(10, 0, 0, 0, unit = "pt"),
      family = "unica"))

ggsave("isometric-bw-2.png")
```

## Another variation

Use the whole grid but with different tiles in parts:
```{r}
coords <-  expand.grid(x = seq(0, 10 * sqrt(3), sqrt(3)),
                       y = seq(0, 11, 3)) %>%
  rbind(expand.grid(x = seq(sqrt(3)/2, 11 * sqrt(3), sqrt(3)),
                    y = seq(1 + 1/2, 11, 3)))

coords_1 <- coords %>%
  filter(sqrt((x - 5 * sqrt(3))^2 + (y - 5)^2) <= 4.3)

coords_2 <- coords %>%
  filter(sqrt((x - 5 * sqrt(3))^2 + (y - 5)^2) > 4.3)

x_c <- coords_1$x
y_c <- coords_1$y

mosaic_1 <- map2_dfr(.x = x_c, .y = y_c, ~cube_up(.x, .y)) 


x_c <- coords_2$x
y_c <- coords_2$y

mosaic_2 <- map2_dfr(.x = x_c, .y = y_c, ~cube_down(.x, .y)) 

mosaic_1 %>% 
  ggplot() +
  geom_sf(aes(fill = id),
          color = "white")

mosaic_2 %>% 
  ggplot() +
  geom_sf(aes(fill = id),
          color = "white")
```

Intersect the lines with faces of the polygons:
```{r}
# Mosaic 1
lines_v_intersect_1 <- lines_v %>%
  st_intersection(mosaic_1 %>%
                    filter(id == "right"))

lines_dr_intersect_1 <- lines_dr %>%
  st_intersection(mosaic_1 %>%
                    filter(id == "left"))

lines_dl_intersect_1 <- lines_dl %>%
  st_intersection(mosaic_1 %>%
                    filter(id == "top"))

lines_intersect_1 <- rbind(lines_v_intersect_1,
                         lines_dr_intersect_1,
                         lines_dl_intersect_1)

# Mosaic 2
lines_v_intersect_2 <- lines_v %>%
  st_intersection(mosaic_2 %>%
                    filter(id == "left"))

lines_dr_intersect_2 <- lines_dr %>%
  st_intersection(mosaic_2 %>%
                    filter(id == "right"))

lines_dl_intersect_2 <- lines_dl %>%
  st_intersection(mosaic_2 %>%
                    filter(id == "bottom"))

lines_intersect_2 <- rbind(lines_v_intersect_2,
                         lines_dr_intersect_2,
                         lines_dl_intersect_2)

ggplot() +
  geom_sf(data = lines_intersect_1,
          aes(color = id))

ggplot() +
  geom_sf(data = lines_intersect_2,
          aes(color = id))
```

Make pretty:
```{r}
ggplot() +
  # geom_sf(data = mosaic_1,
  #         fill = "black",
  #         color = "white") +
  # geom_sf(data = mosaic_2,
  #         fill = "black",
  #         color = "white") +
  geom_sf(data = lines_intersect_1 %>%
            filter(id != "left"),
          color = "white",
          size = 0.5) +
  geom_sf(data = lines_intersect_2 %>%
            filter(id != "right"),
          color = "white",
          size = 0.5) +
  labs(title = "Isometric Perspective", caption = "@paezha") +
  theme_void() +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "black"),
        plot.title = element_text(
      size = rel(5), margin = margin(0, 0, 5, 0, unit = "pt"),
      family = "monoton", face = "bold"),
    plot.subtitle = element_text(
      size = rel(8), margin = margin(0, 0, 10, 0, unit = "pt"),
      family = "unica"),
    plot.caption = element_text(
      size = rel(5), margin = margin(10, 0, 0, 0, unit = "pt"),
      family = "unica"))

ggsave("isometric-bw-3.png")
```

## Another variation

Use the whole grid but with different tiles in parts:
```{r}
coords <-  expand.grid(x = seq(0, 10 * sqrt(3), sqrt(3)),
                       y = seq(0, 11, 3)) %>%
  rbind(expand.grid(x = seq(sqrt(3)/2, 11 * sqrt(3), sqrt(3)),
                    y = seq(1 + 1/2, 11, 3)))

coords_1 <- coords %>%
  slice_sample(prop = 0.5)

coords_2 <- coords %>%
  anti_join(coords_1)

x_c <- coords_1$x
y_c <- coords_1$y

mosaic_1 <- map2_dfr(.x = x_c, .y = y_c, ~cube_up(.x, .y)) 


x_c <- coords_2$x
y_c <- coords_2$y

mosaic_2 <- map2_dfr(.x = x_c, .y = y_c, ~cube_down(.x, .y)) 

mosaic_1 %>% 
  ggplot() +
  geom_sf(aes(fill = id),
          color = "white")

mosaic_2 %>% 
  ggplot() +
  geom_sf(aes(fill = id),
          color = "white")
```

Intersect the lines with faces of the polygons:
```{r}
# Mosaic 1
lines_v_intersect_1 <- lines_v %>%
  st_intersection(mosaic_1 %>%
                    filter(id == "right"))

lines_dr_intersect_1 <- lines_dr %>%
  st_intersection(mosaic_1 %>%
                    filter(id == "left"))

lines_dl_intersect_1 <- lines_dl %>%
  st_intersection(mosaic_1 %>%
                    filter(id == "top"))

lines_intersect_1 <- rbind(lines_v_intersect_1,
                         lines_dr_intersect_1,
                         lines_dl_intersect_1)

# Mosaic 2
lines_v_intersect_2 <- lines_v %>%
  st_intersection(mosaic_2 %>%
                    filter(id == "left"))

lines_dr_intersect_2 <- lines_dr %>%
  st_intersection(mosaic_2 %>%
                    filter(id == "right"))

lines_dl_intersect_2 <- lines_dl %>%
  st_intersection(mosaic_2 %>%
                    filter(id == "bottom"))

lines_intersect_2 <- rbind(lines_v_intersect_2,
                         lines_dr_intersect_2,
                         lines_dl_intersect_2)

ggplot() +
  geom_sf(data = lines_intersect_1,
          aes(color = id))

ggplot() +
  geom_sf(data = lines_intersect_2,
          aes(color = id))
```

Make pretty:
```{r}
ggplot() +
  # geom_sf(data = mosaic_1,
  #         fill = "black",
  #         color = "white") +
  # geom_sf(data = mosaic_2,
  #         fill = "black",
  #         color = "white") +
  geom_sf(data = lines_intersect_1 %>%
            filter(id != "left"),
          color = "white",
          size = 0.5) +
  geom_sf(data = lines_intersect_2 %>%
            filter(id != "right"),
          color = "white",
          size = 0.5) +
  labs(title = "Isometric Perspective", caption = "@paezha") +
  theme_void() +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "black"),
        plot.title = element_text(
      size = rel(5), margin = margin(0, 0, 5, 0, unit = "pt"),
      family = "monoton", face = "bold"),
    plot.subtitle = element_text(
      size = rel(8), margin = margin(0, 0, 10, 0, unit = "pt"),
      family = "unica"),
    plot.caption = element_text(
      size = rel(5), margin = margin(10, 0, 0, 0, unit = "pt"),
      family = "unica"))

ggsave("isometric-bw-4.png")
```

