---
title: "More experiments packing shapes"
---

```{r load-packages, cache = FALSE, warning=FALSE, message=FALSE}
library(ggforce)
library(ggimage)
library(lwgeom)
library(MexBrewer)
library(sf)
library(tidyverse)
```

Create a polygon of the stipulated dimensions:
```{r}
container <- matrix(c(0, 0, 
                       0, 12, 
                       8, 12,  
                       8, 0,
                       0, 0),
                     ncol = 2,
                     byrow = TRUE)

# Convert coordinates to polygons and then to simple features
container <- data.frame(id = 1,
                        r = NA,
                 geometry = st_polygon(list(container)) %>% 
                   st_sfc()) %>% 
  st_as_sf() %>% 
  st_cast(to = "MULTILINESTRING")
```

Plot this initial container:
```{r}
ggplot() + 
  geom_sf(data = container)
```

The inputs for the packing algorithm are:

- An sf object with multilinestring.
- Parameters for generating the circles:
    - Maximum number of circles
    - Maximum radius for a circle
    - Minimum radius for a circle

Function for packing:
```{r}
st_circle_packer <- function(p, max_circles = 100, max_radius = 1, min_radius = 0.1){
  
  # Initialize the table with circles
  circles <- data.frame()
  
  # Convert lines to polygons
  p_polygons <- p %>%
    st_cast(to = "POLYGON")
  
  # Create initial set of points for potential circles in the space of the bounding box of the polygons
  region <- st_bbox(p)
  c_points <- data.frame(x = runif(n = max_circles,
                                   min = region[1],
                                   max = region[3]),
                         y = runif(n = max_circles,
                                   min = region[2],
                                   max = region[4]))
  
  # Convert the points to simple features and add a unique point identifier (PID)
  c_points <- c_points %>%
    st_as_sf(coords = c("x", "y")) %>%
    mutate(PID = 1:n())
  
  # Find any points that fall outside of a polygon and remove
  c_points <- c_points %>%
    st_join(p_polygons) %>%
    drop_na(id)
  
  # Initialize stopping criterion
  stopping_criterion <- TRUE
  
  while(stopping_criterion){
    # Sample one point from each polygon: these points are candidates for circles
    circle_candidates <- c_points %>% 
      group_by(id) %>%
      slice_sample(n =1) %>%
      ungroup()
    
    # Remove the points sampled from the table of points so that they are not considered again in the future
    c_points <- c_points %>%
      anti_join(circle_candidates %>%
                  st_drop_geometry() %>%
                  select(PID),
                by = "PID")
    
    # Find the distance of the candidate points to the boundaries of the polygons if no circles exist yet
    if(nrow(circles) == 0){
      circle_candidates$r <- circle_candidates %>%
        st_distance(p) %>% 
        data.frame() %>%
        apply(1, min)
    }# Find the distance of the candidate points to the boundaries of the polygons and circles if they exist
    else{
      circle_candidates$r <- circle_candidates %>%
        st_distance(rbind(p, 
                          circles %>%
                            select(-PID))) %>% 
        data.frame() %>%
        apply(1, min)
    }
    
    # Filter candidates with a radius greater than the minimum
    circle_candidates <- circle_candidates %>% 
      filter(r >= min_radius)
    
    # Make sure that the radius does not exceed the maximum
    circle_candidates <- circle_candidates %>%
      mutate(r = ifelse(r >= max_radius, max_radius, r))
    
    # If there are candidates points with a radius above the tolerance then create circles
    if(nrow(circle_candidates) > 0){
      # Use the points and buffers to create circles that are added to the existing table of circles
      circles <- rbind(circles,
                       circle_candidates %>%
                         st_buffer(dist = circle_candidates$r))
      
      # Clear points that are now _inside_ a circle from the candidates (the radius will _not_ be NA)
      c_points <- c_points %>%
        select(-c(r)) %>% 
        st_join(circles %>%
                  select(r)) %>%
        filter(is.na(r))
    }
    stopping_criterion <- nrow(c_points) > 0
  }
  return(circles)
}
```

Create a first pack:
```{r}
circles_1 <- container %>%
  st_circle_packer(max_circles = 3000, 
                   max_radius = 4,
                   min_radius = 0.1)
```

Plot:
```{r}
ggplot() + 
  geom_sf(data = container, 
          aes(fill = factor(id))) +
  geom_sf(data = circles_1,
          fill = NA)
```

Extract centroids and radii of the circles to plot as triangles:
```{r}
triangles <- data.frame(circles_1 %>% 
                            st_drop_geometry(),
                          st_centroid(circles_1) %>% 
                            st_coordinates())
triangles_1 <- triangles %>%
  filter(r >= 0.5)

triangles_2 <- triangles %>%
  filter(r < 0.5)
```

Use {ggforce} to plot as triangles
```{r}
ggplot() +
  geom_regon(data = triangles_2,
             aes(x0 = X,
                 y0 = Y, 
                 sides = 3,
                 angle = 45, 
                 r = r)) +
  geom_sf(data = circles_1 %>%
            filter(r > 0.5),
          fill = "white") + 
  theme_void()

#ggsave(filename = "800x80-1.png")
```
Plot all triangles:
```{r}
ggplot() +
  geom_regon(data = triangles_1,
             aes(x0 = X,
                 y0 = Y, 
                 sides = 3,
                 angle = 45, 
                 r = r)) +
  geom_regon(data = triangles_2,
             aes(x0 = X,
                 y0 = Y, 
                 sides = 3,
                 angle = 0, 
                 r = r),
             fill = "white",
             color = "black") +
  coord_equal() +
  theme_void()
```

Next I'd like to pack circles in the bigger circles of the first pack and turn them into triangles. First convert to lines and select those with a radius greater than 10:
```{r}
circles_lines <- circles_1 %>%
  st_cast(to = "MULTILINESTRING") %>%
  filter(r >= 0.5)
```

Plot:
```{r}
ggplot() + 
  geom_sf(data = container, 
          aes(fill = factor(id))) +
  geom_sf(data = circles_lines,
          fill = NA)
```

Now pack those circles:
```{r}
triangles_level2 <- circles_lines %>% 
  transmute(id = 1:nrow(circles_lines), # Reset ids
            r = NA) %>% # set radius to NA
  st_circle_packer(max_circles = 3000, 
                   max_radius = 1,
                   min_radius = 0.01)
```

Prepare for plotting as triangles:
```{r}
triangles_level2 <- data.frame(triangles_level2 %>% 
                            st_drop_geometry(),
                          st_centroid(triangles_level2) %>% 
                            st_coordinates())
```

Plot
```{r}
ggplot() +
  geom_regon(data = triangles_level2,
             aes(x0 = X,
                 y0 = Y, 
                 sides = 3,
                 angle = 45, 
                 r = r),
             fill = "white",
             color = "red") +
  geom_regon(data = triangles_2,
             aes(x0 = X,
                 y0 = Y, 
                 sides = 3,
                 angle = 0, 
                 r = r),
             fill = "black",
             color = "black") +
  coord_equal() +
  theme_void()
```

```{r}
set.seed(2017-02-21)
d <- data.frame(x = rnorm(10),
                y = rnorm(10),
                image = c("cherry-blossom-icon.png"),
                size = runif(10, 0.05, 0.25))

ggplot(d, aes(x, y)) + geom_image(aes(image=image, size = I(size))) +coord_equal()
```

```{r}
col_palette <- MetBrewer::met.brewer("Hokusai1")
ggplot() +
  geom_sf(data = container %>%
            st_cast(to = "POLYGON"),
          color = NA,
          fill = col_palette[4]) +
  geom_regon(data = triangles_2 %>%
               mutate(c = factor(sample.int(7, 
                                            n(), 
                                            replace = TRUE)), 
                      ordered = TRUE),
             aes(x0 = X,
                 y0 = Y, 
                 sides = 3,
                 angle = 45, 
                 r = r,
                 fill = c),
             color = "white") +
  geom_image(data = triangles_1  %>%
            mutate(image = "cherry-blossom-icon-3.png"),
             aes(image = image,
                 x = X,
                 y = Y, 
                 size = I(r) * 0.15)) +
  scale_fill_manual(values = col_palette) +
  #coord_equal() +
  theme_void()

#ggsave(filename = "800x80-1.png")
```

I got some carps and removed the background with https://tools.picsart.com/background-removal/ or https://www.remove.bg/upload.

```{r}
col_palette <- MetBrewer::met.brewer("Hokusai2")

ggplot() +
  geom_sf(data = container %>%
            st_cast(to = "POLYGON"),
          color = NA,
          fill = col_palette[6]) +
  geom_circle(data = triangles_2 %>%
               mutate(c = factor(sample.int(6, 
                                            n(), 
                                            replace = TRUE)), 
                      ordered = TRUE),
             aes(x0 = X,
                 y0 = Y, 
                 r = r,
                 fill = c),
             color = col_palette[1]) +
  geom_image(data = triangles_1  %>%
            mutate(image = sample(c("carp-pair-1.png",
                                    "carp-pair-2.png"),
                                  size = n(),
                                  replace = TRUE)),
             aes(image = image,
                 x = X,
                 y = Y, 
                 size = I(r) * 0.10)) +
  scale_fill_manual(values = col_palette) +
  #coord_equal() +
  theme_void() +
  theme(legend.position = "none")

ggsave(filename = "packing-carps-hokusai-2.png", 
       width = 7, 
       height = 7, 
       units = "in")
```

Different color palette:
```{r}
col_palette <- MetBrewer::met.brewer("Hokusai1")

ggplot() +
  geom_sf(data = container %>%
            st_cast(to = "POLYGON"),
          color = NA,
          fill = col_palette[7]) +
  geom_circle(data = triangles_2 %>%
               mutate(c = factor(sample.int(7, 
                                            n(), 
                                            replace = TRUE)), 
                      ordered = TRUE),
             aes(x0 = X,
                 y0 = Y, 
                 r = r,
                 fill = c),
             color = col_palette[1]) +
  geom_image(data = triangles_1  %>%
            mutate(image = sample(c("carp-pair-1.png",
                                    "carp-pair-2.png"),
                                  size = n(),
                                  replace = TRUE)),
             aes(image = image,
                 x = X,
                 y = Y, 
                 size = I(r) * 0.10)) +
  scale_fill_manual(values = col_palette) +
  #coord_equal() +
  theme_void() +
  theme(legend.position = "none")

ggsave(filename = "packing-carps-hokusai-1.png", 
       width = 7, 
       height = 7, 
       units = "in")
```

## Make fun shapes

Take the original container and pass a line through it to partition it. Create a data frame for these lines:
```{r}
df_lines <- data.frame(x = seq(0,
                               8,
                               0.1))
```

Function for lines:
```{r}
df_lines <- df_lines %>%
  mutate(line_1 = - 0 + 10/(1 + exp(-1 * x + 6)),
         line_2 = 2 + 10/(1 + exp(-1.3 * x + 4)))
```


```{r}
ggplot() +
  geom_sf(data = container) +
  geom_line(data = df_lines,
            aes(x = x, 
                y = line_1)) +
  geom_line(data = df_lines,
            aes(x = x, 
                y = line_2),
            color = "blue")
```

Convert lines to simple features:
```{r}
line_1 <- matrix(c(df_lines$x,
                   df_lines$line_1),
                 nrow = nrow(df_lines),
                 byrow = FALSE)

line_2 <- matrix(c(df_lines$x,
                   df_lines$line_2),
                 nrow = nrow(df_lines),
                 byrow = FALSE)

# Convert coordinates to lines and then to simple features
line_1 <- data.frame(id = 1,
                     r = NA,
                     geometry = st_linestring(line_1) %>% 
                   st_sfc()) %>% 
  st_as_sf()

line_2 <- data.frame(id = 2,
                     r = NA,
                     geometry = st_linestring(line_2) %>% 
                   st_sfc()) %>% 
  st_as_sf()

blade <- rbind(line_1,
               line_2)
```

Bind to original container:
```{r}
container_2 <- container %>%
  st_cast(to = "POLYGON") %>%
  st_split(blade)
```

Convert to polygons:
```{r}
container_2 <- container_2 %>%
  st_collection_extract(c("POLYGON")) %>%
  mutate(id = 1:n())
```

Plot:
```{r}
ggplot() +
  geom_sf(data = container_2,
          aes(fill = factor(id)))
```

Now convert to multilinestring:
```{r}
container_2 <- container_2 %>%
  st_cast(to = "MULTILINESTRING")
```

Pack and plot these bad boys!

Plot packed sigmoids `Atentado` style:
```{r}
col_palette <- mex.brewer("Atentado", 
                          n = 30)

circles_1 <- container_2 %>%
  st_circle_packer(max_circles = 3000, 
                   max_radius = 3,
                   min_radius = 0.20)

ggplot() + 
  geom_sf(data = container_2 %>%
            st_cast(to = "POLYGON") %>%
            mutate(c = case_when(id == 1 ~ 5,
                                 id == 2 ~ 15,
                                 id == 3 ~ 25)), 
          aes(fill = c),
          color = NA) +
  geom_sf(data = circles_1 %>%
            mutate(c = case_when(id == 1 ~ runif(n(), 11, 20),
                                 id == 2 ~ runif(n(), 21, 30),
                                 id == 3 ~ runif(n(), 1, 10))),
          aes(fill = c),
          color = "white") +
  scale_fill_gradientn(colors = col_palette) +
  theme_void() + 
  theme(legend.position = "none")

ggsave(filename = "packing-sigmoids-atentado.png", 
       width = 8, 
       height = 12, 
       units = "in")
```

Plot packed sigmoids `Revolucion` style:
```{r}
col_palette <- mex.brewer("Revolucion", 
                          n = 30)

circles_1 <- container_2 %>%
  st_circle_packer(max_circles = 3000, 
                   max_radius = 3,
                   min_radius = 0.20)

ggplot() + 
  geom_sf(data = container_2 %>%
            st_cast(to = "POLYGON") %>%
            mutate(c = case_when(id == 1 ~ 5,
                                 id == 2 ~ 15,
                                 id == 3 ~ 25)), 
          aes(fill = c),
          color = NA) +
  geom_sf(data = circles_1 %>%
            mutate(c = case_when(id == 1 ~ runif(n(), 11, 20),
                                 id == 2 ~ runif(n(), 21, 30),
                                 id == 3 ~ runif(n(), 1, 10))),
          aes(fill = c),
          color = "white") +
  scale_fill_gradientn(colors = col_palette) +
  theme_void() + 
  theme(legend.position = "none")

ggsave(filename = "packing-sigmoids-revolucion.png", 
       width = 8, 
       height = 12, 
       units = "in")
```

Plot packed sigmoids `Alacena` style:
```{r}
col_palette <- mex.brewer("Alacena", 
                          n = 30)
circles_1 <- container_2 %>%
  st_circle_packer(max_circles = 3000, 
                   max_radius = 3,
                   min_radius = 0.20)

ggplot() + 
  geom_sf(data = container_2 %>%
            st_cast(to = "POLYGON") %>%
            mutate(c = case_when(id == 1 ~ 5,
                                 id == 2 ~ 15,
                                 id == 3 ~ 25)), 
          aes(fill = c),
          color = NA) +
  geom_sf(data = circles_1 %>%
            mutate(c = case_when(id == 1 ~ runif(n(), 11, 20),
                                 id == 2 ~ runif(n(), 21, 30),
                                 id == 3 ~ runif(n(), 1, 10))),
          aes(fill = c),
          color = "white") +
  scale_fill_gradientn(colors = col_palette) +
  theme_void() + 
  theme(legend.position = "none")

ggsave(filename = "packing-sigmoids-alacena.png", 
       width = 8, 
       height = 12, 
       units = "in")
```

Plot packed sigmoids `Ronda` style:
```{r}
col_palette <- mex.brewer("Ronda", 
                          n = 30)
circles_1 <- container_2 %>%
  st_circle_packer(max_circles = 3000, 
                   max_radius = 3,
                   min_radius = 0.20)

ggplot() + 
  geom_sf(data = container_2 %>%
            st_cast(to = "POLYGON") %>%
            mutate(c = case_when(id == 1 ~ 5,
                                 id == 2 ~ 15,
                                 id == 3 ~ 25)), 
          aes(fill = c),
          color = NA) +
  geom_sf(data = circles_1 %>%
            mutate(c = case_when(id == 1 ~ runif(n(), 11, 20),
                                 id == 2 ~ runif(n(), 21, 30),
                                 id == 3 ~ runif(n(), 1, 10))),
          aes(fill = c),
          color = "white") +
  scale_fill_gradientn(colors = col_palette) +
  theme_void() + 
  theme(legend.position = "none")

ggsave(filename = "packing-sigmoids-ronda.png", 
       width = 8, 
       height = 12, 
       units = "in")
```

## Enhancements

Modify the function to allow for radius parameters (min/max) to vary by polygon:
```{r}
st_circle_packer <- function(p, max_circles = 100, max_radius = 1, min_radius = 0.1){
  
  # Initialize the table with circles
  circles <- data.frame()
  
  # Initialize table with tolerance parameters
  radius_pars <- data.frame(id = 1:nrow(p), min_radius, max_radius)
  
  # Convert lines to polygons
  p_polygons <- p %>%
    st_cast(to = "POLYGON")
  
  # Create initial set of points for potential circles in the space of the bounding box of the polygons
  region <- st_bbox(p)
  c_points <- data.frame(x = runif(n = max_circles,
                                   min = region[1],
                                   max = region[3]),
                         y = runif(n = max_circles,
                                   min = region[2],
                                   max = region[4]))
  
  # Convert the points to simple features and add a unique point identifier (PID)
  c_points <- c_points %>%
    st_as_sf(coords = c("x", "y")) %>%
    mutate(PID = 1:n())
  
  # Find any points that fall outside of a polygon and remove
  c_points <- c_points %>%
    st_join(p_polygons) %>%
    drop_na(id)
  
  # Initialize stopping criterion
  stopping_criterion <- TRUE
  
  while(stopping_criterion){
    # Sample one point from each polygon: these points are candidates for circles
    circle_candidates <- c_points %>% 
      group_by(id) %>%
      slice_sample(n =1) %>%
      ungroup()
    
    # Remove the points sampled from the table of points so that they are not considered again in the future
    c_points <- c_points %>%
      anti_join(circle_candidates %>%
                  st_drop_geometry() %>%
                  select(PID),
                by = "PID")
    
    # Find the distance of the candidate points to the boundaries of the polygons if no circles exist yet
    if(nrow(circles) == 0){
      circle_candidates$r <- circle_candidates %>%
        st_distance(p) %>% 
        data.frame() %>%
        apply(1, min)
    }# Find the distance of the candidate points to the boundaries of the polygons and circles if they exist
    else{
      circle_candidates$r <- circle_candidates %>%
        st_distance(rbind(p, 
                          circles %>%
                            select(-PID))) %>% 
        data.frame() %>%
        apply(1, min)
    }
    
    # Join the tolerance parameters and filter candidates with a radius greater than the minimum
    circle_candidates <- circle_candidates %>% 
      left_join(radius_pars, by = "id") %>%
      filter(r >= min_radius)
    
    # Make sure that the radius does not exceed the maximum
    circle_candidates <- circle_candidates %>%
      mutate(r = ifelse(r >= max_radius, max_radius, r)) %>%
      select(-c(min_radius, max_radius)) # Drop tolerance parameters from table, no longer needed
    
    # If there are candidates points with a radius above the tolerance then create circles
    if(nrow(circle_candidates) > 0){
      # Use the points and buffers to create circles that are added to the existing table of circles
      circles <- rbind(circles,
                       circle_candidates %>%
                         st_buffer(dist = circle_candidates$r))
      
      # Clear points that are now _inside_ a circle from the candidates (the radius will _not_ be NA)
      c_points <- c_points %>%
        select(-c(r)) %>% 
        st_join(circles %>%
                  select(r)) %>%
        filter(is.na(r))
    }
    stopping_criterion <- nrow(c_points) > 0
  }
  return(circles)
}
```



```{r}
col_palette <- mex.brewer("Atentado", 
                          n = 30)

circles_1 <- container_2 %>%
  st_circle_packer(max_circles = 3000, 
                   max_radius = c(2.5, 1, 0.5),
                   min_radius = c(0.20, 0.1, 0.01))

ggplot() + 
  geom_sf(data = container_2 %>%
            st_cast(to = "POLYGON") %>%
            mutate(c = case_when(id == 1 ~ 5,
                                 id == 2 ~ 15,
                                 id == 3 ~ 25)), 
          aes(fill = c),
          color = NA) +
  geom_sf(data = circles_1 %>%
            mutate(c = case_when(id == 1 ~ runif(n(), 11, 20),
                                 id == 2 ~ runif(n(), 21, 30),
                                 id == 3 ~ runif(n(), 1, 10))),
          aes(fill = c),
          color = "white") +
  scale_fill_gradientn(colors = col_palette) +
  theme_void() + 
  theme(legend.position = "none")

ggsave(filename = "packing-sigmoids-2-atentado.png", 
       width = 8, 
       height = 12, 
       units = "in")
```

## Try with an underlying image (check this out: https://twitter.com/saurabhdhiman/status/1488268698703912961?s=20&t=HAQgcp8Sxw1lbdhpU-ltjw)

Load packages:
```{r}
library(imager)
```

## Snowscape

Read the image using `imager::load.image()`:
```{r}
snowscape <- load.image("snowscape.jpg")
```

Check the size of the image: 
```{r}
summary(snowscape)
```

Convert image to data frame (still working with {imager}):
```{r}
snowscape_df <- snowscape %>%
  as.data.frame(wide="c") %>% 
  mutate(color = rgb(c.1,
                     c.2,
                     c.3))
```

Plot image:
```{r}
plot(snowscape)
```


Create a circle to serve as container, centered on the sun:
```{r}
container <- data.frame(x = 650, y = 780) %>%
  st_as_sf(coords = c("x", "y")) %>%
  st_buffer(dist = 650) %>%
  mutate(id = 1:n(),
         r = NA) %>%
  st_cast(to = "MULTILINESTRING")
```

Plot:
```{r}
plot(snowscape)
plot(st_geometry(container), add = TRUE)
```

Pack circles:
```{r}
circles <- container %>%
  st_circle_packer(max_circles = 20000, 
                   max_radius = c(10),
                   min_radius = c(1))
```

Plot:
```{r}
ggplot(circles) +
  geom_sf() + 
  scale_y_reverse()
```

Now find the nearest pixel in the original image to borrow the color. First get the centroids of the circles:
```{r}
circle_centroids <- circles %>%
          st_centroid()
```

Convert the image to sf to use sf functions to find nearest features to borrow colors:
```{r}
snowscape_sf <- snowscape_df %>%
    st_as_sf(coords = c("x", "y"))

```

Find the nearest feature in the original image to borrow the colors:
```{r}
snowscape_colors <- snowscape_df[circle_centroids %>%
                                   st_nearest_feature(snowscape_sf),]
```

Bind the colors to the packed circles:
```{r}
circles <- circles %>%
  mutate(color = snowscape_colors$color)
```

Plot:
```{r}
ggplot() +
  geom_sf(data = circles,
          aes(fill = color),
          color = NA) + 
  scale_y_reverse() +
  scale_fill_identity() + 
  theme_void()

ggsave("snowscape-circle-packing.png")
```


