---
title: "Experiments with Random Walks"
output: html_notebook
---

In this notebook I experiment with random walks.

Load packages:
```{r}
library(ggnewscale)
library(MexBrewer)
library(sf)
library(tidyverse)
```


This example I took from here: https://mikegruz.github.io/articles/2016-12/random-walks:
```{r}
n = 5000

d2.rand.walk = data.frame(
  x = cumsum(sample(c(-1, 1),
                            size=n,
                            replace=TRUE)),
  y = cumsum(sample(c(-1, 1), 
                            size=n, 
                            replace=TRUE)))


ggplot(d2.rand.walk, aes(x=x, y=y)) + 
  geom_path() +  
  coord_equal() +
  theme_minimal()
```

This is my version to allow for steps to happen in more directions:
```{r}
n = 5000

d2.rand.walk = data.frame(
  x = cumsum(1 * cos(sample(seq(0,
                                7/4 * pi, 
                                by = 1/4 * pi), 
                            size=n, 
                            replace=TRUE))),
  y = cumsum(1 * sin(sample(seq(0,
                                7/4 * pi, 
                                by = 1/4 * pi), 
                            size=n, replace=TRUE))))


ggplot(d2.rand.walk, aes(x=x, y=y)) + 
  geom_path() +  
  coord_equal() +
  theme_minimal()
```
Simulating the whole random walk simultaneously is quick, but offers no control over its path. But I am interested in a random walk that is limited to a polygon. 

Here is an example of a heart-shaped polygon given by parametric equations:
```{r}
df <- data.frame(t = seq(0, 2 * pi - 2 * pi/100, 2 * pi/100))

df<- df %>%
  mutate(x	=	16 * sin(t)^3,
         y	=	13 * cos(t) - 5 * cos(2 * t) - 2 * cos(3 * t) - cos(4*t))

df <- rbind(df,
            slice_head(df))

ggplot() +
  geom_path(data = df,
            aes(x = x,
                y = y)) +
  coord_equal()
```

Convert the coordinates to sf to be able to check whether a point is inside or outside of the polygon:
```{r}
heart <- matrix(c(df$x, 
                  df$y), 
                ncol = 2,
                byrow = FALSE)

heart <- st_polygon(list(heart))
```

Create a container polygon:
```{r}

container <- matrix( c(bbox[1] - 2, bbox[2] - 2,
                       bbox[1] - 2, bbox[4] + 2,
                       bbox[3] + 2, bbox[4] + 2,
                       bbox[3] + 2, bbox[2] - 2,
                       bbox[1] - 2, bbox[2] - 2),
                     ncol = 2,
                     byrow = TRUE)

container <- st_polygon(list(container))
```

Carve out the inner polygon:
```{r}
container <- container %>%
  st_difference(heart)
```

Simulate a random walk _in_ the heart-shaped polygon:
```{r}
# Length of walk
n <- 7500

# Step length
step_length <- 1


# Starting point:
rw <- data.frame(x = 0, 
                 y = -14)

for(i in 1:n){
  
  # Initialize search for next candidate step
  candidate_step <- data.frame(x = step_length * cos(sample(seq(0,
                                                                7/4 * pi,
                                                                by = 1/4 * pi),
                                                            1)),
                               y = step_length * sin(sample(seq(0,
                                                                7/4 * pi,
                                                                by = 1/4 * pi),
                                                            1)))

  # candidate_step <- data.frame(x = sample(c(-step_length, step_length), 1),
  #                              y = sample(c(-step_length,step_length), 1))
  
  # Check whether position with candidate step is within polygon
  candidate_position <- slice_tail(rw) %>%
    mutate(x = x + candidate_step$x,
           y = y + candidate_step$y) 
  
  inside_check <- st_within(candidate_position %>% 
               st_as_sf(coords = c("x", "y")),
               heart,
               sparse = FALSE) %>% 
     as.vector()
  
  # If inside bind to to random walk, otherwise reverse position
  if(inside_check){
    rw <- rbind(rw,
                candidate_position)
  }else{
    reverse_position <- slice_tail(rw) %>%
    mutate(x = x - candidate_step$x,
           y = y - candidate_step$y)
    
    rw <- rbind(rw,
                reverse_position)
  }
}
```

Simulate a random walk _outside_ the heart-shaped polygon but _inside_ the frame:
```{r}
# Length of walk
n <- 12500

# Step length
step_length <- 1


# Starting point:
rw_2 <- data.frame(x = -10, 
                 y = -10)

for(i in 1:n){
  
  # Initialize search for next candidate step
  candidate_step <- data.frame(x = step_length * cos(sample(seq(0,
                                                                7/4 * pi,
                                                                by = 1/4 * pi),
                                                            1)),
                               y = step_length * sin(sample(seq(0,
                                                                7/4 * pi,
                                                                by = 1/4 * pi),
                                                            1)))

  # candidate_step <- data.frame(x = sample(c(-step_length, step_length), 1),
  #                              y = sample(c(-step_length,step_length), 1))
  
  # Check whether position with candidate step is within polygon
  candidate_position <- slice_tail(rw_2) %>%
    mutate(x = x + candidate_step$x,
           y = y + candidate_step$y) 
  
  inside_check <- st_within(candidate_position %>% 
               st_as_sf(coords = c("x", "y")),
               container,
               sparse = FALSE) %>% 
     as.vector()
  
  # If inside bind to to random walk, otherwise reverse position
  if(inside_check){
    rw_2 <- rbind(rw_2,
                candidate_position)
  }else{
    reverse_position <- slice_tail(rw_2) %>%
    mutate(x = x - candidate_step$x,
           y = y - candidate_step$y)
    
    rw_2 <- rbind(rw_2,
                reverse_position)
  }
}
```


Plot random walk:
```{r}
col_palette <- mex.brewer("Alacena")[6:10]
col_palette_2 <- mex.brewer("Alacena")[1:5]

bbox <- st_bbox(heart)

ggplot() +
  geom_sf(data = heart) +
   geom_rect(aes(xmin = bbox[1] - 2, 
                 xmax = bbox[3] + 2, 
                 ymin = bbox[2] - 2 , 
                 ymax = bbox[4] + 2),
             fill = "black") +
  geom_path(data = rw_2, 
       aes(x = x, 
           y = y,
           color = x - y)) +
  scale_color_gradientn(colors = col_palette) +
  new_scale_color() +
  geom_path(data = rw, 
        aes(x = x, 
            y = y,
            color = x - y)) +
  scale_color_gradientn(colors = col_palette_2) +
  #coord_equal() + 
  theme_void() + 
  theme(legend.position = "none")
```




