---
title: "R Notebook"
output: html_notebook
---

Today I will use the following packages:
```{r load-packages, cache = FALSE, warning=FALSE, message=FALSE}
library(ggforce)
#library(geomtextpath)
library(lwgeom)
library(MexBrewer)
library(sf)
library(tidyverse)
```

## Creating a seascape

Create a polygon of to become the frame for my "landscape":
```{r}
container_polygon <- matrix(c(0, 0, 
                              0, 8, 
                              12, 8,  
                              12, 0,
                              0, 0),
                            ncol = 2,
                            byrow = TRUE)

# Convert coordinates to polygons and then to simple features
container_polygon <- data.frame(id = 1,
                                r = NA,
                                geometry = st_polygon(list(container_polygon)) %>% 
                                  st_sfc()) %>% 
  st_as_sf()
```

Plot this initial container:
```{r}
ggplot() + 
  geom_sf(data = container_polygon)
```

Make waves:
```{r}
# Initialize data frame
df_lines <- data.frame(x = seq(0,
                               12,
                               0.1))

# Initialize position in y
vjust <- seq(0.5, 6, 0.2)

# Initialize amplitude of waves
Amax <- 0.5
Amin <- 0.1
A <- seq(Amin, Amax, (Amax - Amin)/length(vjust))[1:length(vjust)]

# Initialize inverse of f
f <- seq(8, 10, 1)

# Initialize phase
phi <- seq(0, 2 * pi, pi/6)


# Initialize counter
count <- 0

# Make waves
for(i in vjust){
  count <- count + 1
  df_lines[[paste0("line_", count, collapse = "")]] <- (A[count] * cos(2 * pi * 1/f[sample.int(length(f), 1)] * df_lines$x + phi[sample.int(length(phi), 1)]) + vjust[count])
}

# Pivot longer
df_lines <- df_lines %>%
  pivot_longer(cols = -x, names_to = "line", values_to = "y")
```

Make "blade for splitting container:
```{r}
df_blade <- df_lines %>%
  group_by(x) %>%
  summarize(y = max(y),
            .groups = "drop")
```

Turn blade to sf:
```{r}
blade <- matrix(c(df_blade$x,
                  df_blade$y),
                nrow = nrow(df_blade),
                byrow = FALSE)

# Convert coordinates to lines and then to simple features
blade <- data.frame(id = 1,
                    geometry = st_linestring(blade) %>% 
                      st_sfc()) %>% 
  st_as_sf()
```

Split original container:
```{r}
container_2 <- container_polygon %>%
  st_split(blade)
```

Extract polygons and give them new ids:
```{r}
container_2 <- container_2 %>%
  st_collection_extract(c("POLYGON")) %>%
  mutate(id = 1:n())
```

Separate container for sky and smash the rest. 
```{r}
container_sky <- container_2 %>%
  filter(id == 2)

# Initialize container
container_sea_2 <- container_2 %>%
  filter(id == 1)

for(i in 1:length(vjust)){
  # Recreate blade
  df_blade <- df_lines %>%
    filter(line == paste0("line_", i, collapse = ""))
  
  blade <- matrix(c(df_blade$x,
                    df_blade$y),
                  nrow = nrow(df_blade),
                  byrow = FALSE)
  
  # Convert coordinates to lines and then to simple features
  blade <- data.frame(id = 1,
                      geometry = st_linestring(blade) %>% 
                        st_sfc()) %>% 
    st_as_sf()
  
  # Split the container for the sea
  container_sea_2 <- container_sea_2 %>%
                           st_split(blade) %>%
                           st_collection_extract(c("POLYGON")) %>%
                           mutate(id = 1:n())
  
}
```

Sea background:
```{r}
container_sea_2_bkg <- container_sea_2 %>%
  mutate(geometry = st_geometry(container_sea_2) + c(-0.1, 0.05)) %>%
  st_intersection(container_polygon %>% 
                    st_geometry())
  
```
```{r}
container_sea <- rbind(container_sea_2 %>%
                         mutate(r = "foreground"),
                       container_sea_2_bkg %>%
                         mutate(r = "background")) %>%
  arrange(id, r)
```

```{r}
library(sf)
outer = matrix(c(0,0,10,0,10,10,0,10,0,0),ncol=2, byrow=TRUE)
hole1 = matrix(c(1,1,1,2,2,2,2,1,1,1),ncol=2, byrow=TRUE)
hole2 = matrix(c(5,5,5,6,6,6,6,5,5,5),ncol=2, byrow=TRUE)
pts = list(outer, hole1, hole2)
pl1 = st_geometry(container_sea_2)

plot(pl1)
```
```{r}
pl2 <- st_multipolygon(lapply(pl1, function(x) x[1]))

plot(pl2)
```


```{r}
ggplot() + 
  geom_sf(data = container_sea %>% arrange(id, r), aes(fill = factor(r)))
```

Plot with sea split sequentially:
```{r}
# Color palette
col_palette <- mex.brewer("Atentado")

# Create a sun
# Position of sun
sun_coords <- c(x = runif(1, 2, 9), 
                  y = runif(1, 6, 7))
# Rays
df_sunrays <- data.frame(angle = seq(0, 2*pi, by = 2 * pi / sample(c(6, 8, 10), 1))) %>%
  mutate(x = sun_coords[1] + 1.1 * cos(angle),
         y = sun_coords[2] + 1.1 * sin(angle))

# Plot sky
p <- ggplot() +
  # Plot "sky" polygon
  geom_sf(data = container_sky,
          color = NA,
          fill = col_palette[sample.int(10, 1)]) +
  # Plot "sun"
  with_shadow(geom_regon(aes(x0 = sun_coords[1] + runif(1, -0.05, 0.05),
                 y0 = sun_coords[2] + runif(1, -0.05, 0.05),
                 sides = sample(12:15, 1),
                 angle = 0, r = runif(1, 1.15, 1.45)),
             expand = unit(0.1, 'cm'), radius = unit(0.7, 'cm'),
             fill = col_palette[2]),
             colour = "white",
             x_offset = -3,
             y_offset = -2,
             sigma = 0) +
   with_shadow(geom_regon(aes(x0 = sun_coords[1] + runif(1, -0.05, 0.05),
                 y0 = sun_coords[2] + runif(1, -0.05, 0.05),
                 sides = sample(12:15, 1),
                 angle = 0, r = runif(1, 0.9, 1.1)),
             expand = unit(0.1, 'cm'), radius = unit(0.7, 'cm'),
             fill = col_palette[3]),
             colour = "white",
             x_offset = -3,
             y_offset = -2,
             sigma = 0) +
   with_shadow(geom_regon(aes(x0 = sun_coords[1] + runif(1, -0.05, 0.05),
                 y0 = sun_coords[2] + runif(1, -0.05, 0.05),
                 sides = sample(12:15, 1),
                 angle = 0, r = runif(1, 0.65, 0.85)),
             expand = unit(0.1, 'cm'), radius = unit(0.7, 'cm'),
             fill = col_palette[4]),
             colour = "white",
             x_offset = -3,
             y_offset = -2,
             sigma = 0) +
   with_shadow(geom_regon(data = df_sunrays,
             aes(x0 = x, y0 = y, sides = 3,
                 angle = angle + pi/6, r = 0.2),
             fill = col_palette[4]),
             colour = "white",
             x_offset = -2,
             y_offset = -1,
             sigma = 0)

# Add waves
for(i in 1:nrow(container_sea_2)){
  p <- p + 
    with_shadow(geom_sf(data = container_sea_2[i,],
          aes(fill = id),
          color = NA),
             colour = "white",
             x_offset = -4,
             y_offset = -1,
          sigma = 0)
}

# Finishing details
p <- p +
  scale_color_gradientn(colors = col_palette) +
  scale_fill_gradientn(colors = rev(col_palette)) +
  theme_void() +
  theme(legend.position = "none")

ggsave("wavescapes-atentado.png")
```

Plot with sea split sequentially:
```{r}
# Color palette
col_palette <- mex.brewer("Revolucion")

# Create a sun
# Position of sun
sun_coords <- c(x = runif(1, 2, 9), 
                  y = runif(1, 6, 7))
# Rays
df_sunrays <- data.frame(angle = seq(0, 2*pi, by = 2 * pi / sample(c(6, 8, 10), 1))) %>%
  mutate(x = sun_coords[1] + 1.1 * cos(angle),
         y = sun_coords[2] + 1.1 * sin(angle))

# Plot sky
p <- ggplot() +
  # Plot "sky" polygon
  geom_sf(data = container_sky,
          color = NA,
          fill = col_palette[sample.int(10, 1)]) +
  # Plot "sun"
  with_shadow(geom_regon(aes(x0 = sun_coords[1] + runif(1, -0.05, 0.05),
                 y0 = sun_coords[2] + runif(1, -0.05, 0.05),
                 sides = sample(12:15, 1),
                 angle = 0, r = runif(1, 1.15, 1.45)),
             expand = unit(0.1, 'cm'), radius = unit(0.7, 'cm'),
             fill = col_palette[2]),
             colour = "white",
             x_offset = -3,
             y_offset = -2,
             sigma = 0) +
   with_shadow(geom_regon(aes(x0 = sun_coords[1] + runif(1, -0.05, 0.05),
                 y0 = sun_coords[2] + runif(1, -0.05, 0.05),
                 sides = sample(12:15, 1),
                 angle = 0, r = runif(1, 0.9, 1.1)),
             expand = unit(0.1, 'cm'), radius = unit(0.7, 'cm'),
             fill = col_palette[3]),
             colour = "white",
             x_offset = -3,
             y_offset = -2,
             sigma = 0) +
   with_shadow(geom_regon(aes(x0 = sun_coords[1] + runif(1, -0.05, 0.05),
                 y0 = sun_coords[2] + runif(1, -0.05, 0.05),
                 sides = sample(12:15, 1),
                 angle = 0, r = runif(1, 0.65, 0.85)),
             expand = unit(0.1, 'cm'), radius = unit(0.7, 'cm'),
             fill = col_palette[4]),
             colour = "white",
             x_offset = -3,
             y_offset = -2,
             sigma = 0) +
   with_shadow(geom_regon(data = df_sunrays,
             aes(x0 = x, y0 = y, sides = 3,
                 angle = angle + pi/6, r = 0.2),
             fill = col_palette[4]),
             colour = "white",
             x_offset = -2,
             y_offset = -1,
             sigma = 0)

# Add waves
for(i in 1:nrow(container_sea_2)){
  p <- p + 
    with_shadow(geom_sf(data = container_sea_2[i,],
          aes(fill = id),
          color = NA),
             colour = "white",
             x_offset = -4,
             y_offset = -1,
          sigma = 0)
}

# Finishing details
p <- p +
  scale_color_gradientn(colors = col_palette) +
  scale_fill_gradientn(colors = rev(col_palette)) +
  theme_void() +
  theme(legend.position = "none")

ggsave("wavescapes-revolucion.png")
```
Change color palette:
```{r}
# Color palette
col_palette <- mex.brewer("Alacena")

# Create a sun
# Position of sun
sun_coords <- c(x = runif(1, 2, 9), 
                  y = runif(1, 6, 7))
# Rays
df_sunrays <- data.frame(angle = seq(0, 2*pi, by = 2 * pi / sample(c(8, 10, 12), 1))) %>%
  mutate(x = sun_coords[1] + 1.1 * cos(angle),
         y = sun_coords[2] + 1.1 * sin(angle))

# Plot sky
p <- ggplot() +
  # Plot "sky" polygon
  geom_sf(data = container_sky,
          color = NA,
          fill = col_palette[sample.int(10, 1)]) +
  # Plot "sun"
  with_shadow(geom_regon(aes(x0 = sun_coords[1] + runif(1, -0.05, 0.05),
                 y0 = sun_coords[2] + runif(1, -0.05, 0.05),
                 sides = sample(12:15, 1),
                 angle = 0, r = runif(1, 1.15, 1.45)),
             expand = unit(0.1, 'cm'), radius = unit(0.7, 'cm'),
             fill = col_palette[2]),
             colour = "white",
             x_offset = -3,
             y_offset = -2,
             sigma = 0) +
   with_shadow(geom_regon(aes(x0 = sun_coords[1] + runif(1, -0.05, 0.05),
                 y0 = sun_coords[2] + runif(1, -0.05, 0.05),
                 sides = sample(12:15, 1),
                 angle = 0, r = runif(1, 0.9, 1.1)),
             expand = unit(0.1, 'cm'), radius = unit(0.7, 'cm'),
             fill = col_palette[3]),
             colour = "white",
             x_offset = -3,
             y_offset = -2,
             sigma = 0) +
   with_shadow(geom_regon(aes(x0 = sun_coords[1] + runif(1, -0.05, 0.05),
                 y0 = sun_coords[2] + runif(1, -0.05, 0.05),
                 sides = sample(12:15, 1),
                 angle = 0, r = runif(1, 0.65, 0.85)),
             expand = unit(0.1, 'cm'), radius = unit(0.7, 'cm'),
             fill = col_palette[4]),
             colour = "white",
             x_offset = -3,
             y_offset = -2,
             sigma = 0) +
   with_shadow(geom_regon(data = df_sunrays,
             aes(x0 = x, y0 = y, sides = 3,
                 angle = angle + pi/6, r = 0.2),
             fill = col_palette[4]),
             colour = "white",
             x_offset = -2,
             y_offset = -1,
             sigma = 0)

# Add waves
for(i in 1:nrow(container_sea_2)){
  p <- p + 
    with_shadow(geom_sf(data = container_sea_2[i,],
          aes(fill = id),
          color = NA),
             colour = "white",
             x_offset = -4,
             y_offset = -1,
          sigma = 0)
}

# Finishing details
p <- p +
  scale_color_gradientn(colors = col_palette) +
  scale_fill_gradientn(colors = rev(col_palette)) +
  theme_void() +
  theme(legend.position = "none")

ggsave("wavescapes-alacena.png")
```
