---
title: "R Notebook"
output: html_notebook
---

Here I work with multiscale tiles using a pre-determined tile pattern as opposed to random.

Load packages:
```{r}
library(ambient)
library(ggnewscale)
library(sf)
library(tidyverse)
library(truchet)
```

## Create container for mosaic

To create a data frame with placeholders for the tiles I first select the limits and center of the mosaic:
```{r}
# Extent of mosaic
xlim <- c(0, 21)
ylim <- c(0, 21)

# Center of mosaic
c <- c(10, 10)

# Radius
r1 <- 3.4
r2 <- 15
```

```{r}
container <- expand.grid(x = seq(xlim[1], xlim[2], 1),
                         y = seq(ylim[1], ylim[2], 1))
```

Mutate container to contain specifications of what goes where:
```{r}
container <- container %>%
  filter(sqrt((x - c[1])^2 + (y - c[2])^2) <= r2 & 
           sqrt((x - c[1])^2 + (y - c[2])^2) > r1)
```

Plot:
```{r}
ggplot() + 
  geom_point(data = container,
             aes(x = x, y = y)) + coord_equal()
```

Mutate to add scale of tile to place at each point:
```{r}
# These two variables control where the smaller tiles (scale 1/2) are used
r_scale1 <- 5
r_scale2 <- 9

container <- container %>%
  mutate(scale_p = case_when(sqrt((x - c[1])^2 + (y - c[2])^2) > r_scale2 ~ 1/2,
                             sqrt((x - c[1])^2 + (y - c[2])^2) < r_scale1 ~ 1/2,
                             TRUE ~ 1))
```

Plot:
```{r}
ggplot() + 
  geom_point(data = container,
             aes(x = x, y = y, color = factor(scale_p))) + 
  coord_equal()
```

## Create tiles and assemble mosaic

Create truchet tiles:
```{r}
t1 <- st_truchet_p(type = "-")
t2 <- st_truchet_p(type = "-", scale_p = 1/2)
```

Create mosaic:
```{r}
df <- container
mosaic <- st_truchet_ms(t1 = t1, t2 = t2, df = df)
```

Create ring to intersect the mosaic in clean circles:
```{r}
bf1<- data.frame(geometry = st_geometry(st_point(x = c(c[1], c[2])) %>%
                                          st_buffer(dist = 3.6))) %>% st_sf()

bf2 <- data.frame(geometry = st_geometry(st_point(x = c(c[1], c[2])) %>%
                                           st_buffer(dist = 10.5))) %>% st_sf()

bf <- st_difference(bf2, bf1)
```

## Make pretty alternative 1

Create noisy background:
```{r}
perlin_noise <- long_grid(
  x = seq(xlim[1] - 1, xlim[2], length.out = 1000),
  y = seq(ylim[1] -1, ylim[2], length.out = 1000)) %>%
  mutate(
    noise = fracture(
      gen_perlin, fbm, octaves = 8, frequency = 80, x = x, y = y))
```

Set the noise gradient:
```{r}
noise_gradient <- (grDevices::colorRampPalette(c("#D90368", "#FFD400")))(2)
```

```{r}
ggplot() +
  geom_raster(data = perlin_noise, aes(x, y, fill = noise)) +
  scale_fill_gradientn(colours = noise_gradient) +
  ggnewscale::new_scale_fill() +
  geom_sf(data = mosaic %>%
            st_intersection(bf),
          aes(fill = factor(color)),
          color = "#F1E9DA") +
  scale_fill_manual(values = c("#2E294E", "#541388")) +
  theme_void() +
  theme(legend.position = "none")
```

## Make pretty alternative 2:

Create noisy background:
```{r}
perlin_noise <- long_grid(
  x = seq(xlim[1] - 1, xlim[2], length.out = 1000),
  y = seq(ylim[1] -1, ylim[2], length.out = 1000)) %>%
  mutate(
    noise = fracture(
      gen_perlin, fbm, octaves = 8, frequency = 80, x = x, y = y))
```

Set the noise gradient:
```{r}
noise_gradient <- (grDevices::colorRampPalette(c("#2E294E", "#541388")))(2)
```

```{r}
ggplot() +
  geom_raster(data = perlin_noise, aes(x, y, fill = noise)) +
  scale_fill_gradientn(colours = noise_gradient) +
  ggnewscale::new_scale_fill() +
  geom_sf(data = mosaic %>%
            st_intersection(bf),
          aes(fill = factor(color)),
          color = "#D90368") +
  scale_fill_manual(values = c("#F1E9DA", "#FFD400")) +
  theme_void() +
  theme(legend.position = "none")

#ggsave("truchet-voronoi-concha-tierra.png")
```



## Make pretty alternative 3:

Create noisy background:
```{r}
perlin_noise <- long_grid(
  x = seq(xlim[1] - 1, xlim[2], length.out = 1000),
  y = seq(ylim[1] -1, ylim[2], length.out = 1000)) %>%
  mutate(
    noise = fracture(
      gen_perlin, fbm, octaves = 8, frequency = 80, x = x, y = y))
```

Set the noise gradient:
```{r}
noise_gradient <- (grDevices::colorRampPalette(c("white", "black")))(50)
```

```{r}
ggplot() +
  geom_raster(data = perlin_noise, aes(x, y, fill = noise)) +
  scale_fill_gradientn(colours = noise_gradient) +
  ggnewscale::new_scale_fill() +
  geom_sf(data = mosaic %>%
            st_intersection(bf),
          aes(fill = factor(color)),
          color = NA) +
  scale_fill_manual(values = c("black", "white")) +
  theme_void() +
  theme(legend.position = "none")

#ggsave("truchet-voronoi-concha-tierra.png")
```
