---
title: "R Notebook"
output: html_notebook
---

Here I work with multiscale tiles using a pre-determined tile pattern as opposed to random.

Load packages:
```{r}
#library(ambient)
#library(ggnewscale)
library(sf)
library(tidyverse)
library(truchet)
```

## Create container for mosaic

To create a data frame with placeholders for the tiles I first select the limits and center of the mosaic:
```{r}
# Extent of mosaic
xlim <- c(0, 9)
ylim <- c(0, 2)

# Center of mosaic
c <- c(10, 10)

# Radius
r1 <- 3.4
r2 <- 15
```


```{r}
container <- expand.grid(x = seq(xlim[1], xlim[2], 2),
                         y = c(0, 2))
```


```{r}

x_c <- container$x
y_c <- container$y
type <- c("dl", "dr", "-", "|", "fnw", "fne", "fsw", "fse", "ane", "asw")
scale_p <- rep(1, nrow(container))

#mosaic <- map2_dfr(.x = x_c, .y = y_c, ~st_truchet_p(.x, .y))

pmap_dfr(list(x_c, y_c, type, scale_p), st_truchet_p) %>%
  ggplot() + 
  geom_sf(aes(fill = factor(color)))

pmap_dfr(list(x_c, y_c, type, scale_p/2), st_truchet_p) %>%
  ggplot() + 
  geom_sf(aes(fill = factor(color)))

pmap_dfr(list(x_c, y_c, type, scale_p/4), st_truchet_p) %>%
  ggplot() + 
  geom_sf(aes(fill = factor(color)))
```

## Single scale mosaic (at scale 1)

Define size of container:
```{r}
# Extent of mosaic
xlim <- c(0, 10)
ylim <- c(0, 5)
```

Create container:
```{r}
container <- expand.grid(x = seq(xlim[1], xlim[2], 1),
                         y = seq(xlim[1], xlim[2], 1))
```

Use {purrr} to assemble mosaic:
```{r}

x_c <- container$x
y_c <- container$y
type <- sample(c("dl", "dr"), 121, replace = TRUE)
scale_p <- rep(1, nrow(container))

#mosaic <- map2_dfr(.x = x_c, .y = y_c, ~st_truchet_p(.x, .y))

pmap_dfr(list(x_c, y_c, type, scale_p), st_truchet_p) %>%
  ggplot() + 
  geom_sf(aes(fill = factor(color)),
          color = NA)
```

## Mosaic with tiles at multiple scales

Define size of mosaic:
```{r}
# Extent of mosaic
xlim <- c(0, 10)
ylim <- c(0, 10)
```

Create container:
```{r}
container <- expand.grid(x = seq(xlim[1], xlim[2], 1),
                         y = seq(xlim[1], xlim[2], 1))
```

Adjust container to accommodate tiles at multiple scales:
```{r}
container <- container %>%
  mutate(scale_p = sample(c(1/4), n(), replace = TRUE))

container_2 <- container %>% 
  filter(scale_p == 1/2) %>%
  mutate(x_1 = -0.25, y_1 = 0.25,
         x_2 = 0.25, y_2 = 0.25, 
         x_3 = 0.25, y_3 = -0.25, 
         x_4 = 0.25, y_4 = -0.25) %>%
  pivot_longer(cols = starts_with("x_"),
               names_to = "xpos",
               values_to = "x_shift") %>%
  pivot_longer(cols = starts_with("y_"),
               names_to = "ypos",
               values_to = "y_shift") %>%
  transmute(x = x + x_shift,
         y = y + y_shift,
         scale_p) %>%
  distinct()

container_3 <- container %>% 
  filter(scale_p == 1/4) %>%
  mutate(x_1 = -1/6 * 2, y_1 = 1/6 * 2,
         x_2 = -1/6, y_2 = 1/6 * 2, 
         x_3 = 1/6, y_3 = 1/6 * 2, 
         x_4 = 1/6 * 2, y_4 = 1/6 * 2,
         x_5 = -1/6 * 2, y_5 = 1/6,
         x_6 = -1/6, y_6 = 1/6, 
         x_7 = 1/6, y_7 = 1/6, 
         x_8 = 1/6 * 2, y_8 = 1/6,
         x_9 = -1/6 * 2, y_9 = -1/6 ,
         x_10 = -1/6, y_10 = -1/6, 
         x_11 = 1/6, y_11 = -1/6, 
         x_12 = 1/6 * 2, y_12 = -1/6,
         x_13 = -1/6 * 2, y_13 = -1/6 * 2,
         x_14 = -1/6, y_14 = -1/6 * 2, 
         x_15 = 1/6, y_15 = -1/6 * 2, 
         x_16 = 1/6 * 2, y_16 = -1/6 * 2) %>%
  pivot_longer(cols = starts_with("x_"),
               names_to = "xpos",
               values_to = "x_shift") %>%
  pivot_longer(cols = starts_with("y_"),
               names_to = "ypos",
               values_to = "y_shift") %>%
  transmute(x = x + x_shift,
         y = y + y_shift,
         scale_p) %>%
  distinct()

container <- container %>%
   filter(scale_p == 1) %>%
   rbind(container_2,
         container_3)
```

Plot placeholders for tiles:
```{r}

container  %>%
ggplot() +
  geom_point(aes(x, 
                 y,
                 color = factor(scale_p)))
```

Assemble mosaic:
```{r}
x_c <- container$x
y_c <- container$y
type <- sample(c("dl", "dr", "fsw", "fse", "fnw", "fne", "|", "-"),
               nrow(container), 
               replace = TRUE)
scale_p <- container$scale_p

pmap_dfr(list(x_c, y_c, type, scale_p), st_truchet_p) %>%
  ggplot() + 
  geom_sf(aes(fill = factor(color)),
          color = NA)
```

