---
title: "Truchet Tiles"
output: html_notebook
---

Truchet tiles. See: https://en.wikipedia.org/wiki/Truchet_tiles

I need the following elements: 2 points and one square tile.

Load packages:

```{r load-packages, cache = FALSE, warning=FALSE, message=FALSE}
#library(ggforce)
#library(ggimage)
#library(lwgeom)
library(gganimate)
library(MexBrewer)
library(sf)
library(tidyverse)
```

Create a one-by-one tile:
```{r}
tile <- matrix(c(0, 0, 
                 0, 1, 
                 1, 1,  
                 1, 0,
                 0, 0),
               ncol = 2,
               byrow = TRUE)

# Convert coordinates to polygons and then to simple features
tile <- data.frame(id = 1,
                   r = NA,
                   geometry = st_polygon(list(tile)) %>% 
                     st_sfc()) %>% 
  st_as_sf()
```

Plot tile:
```{r}
ggplot() +
  geom_sf(data =  tile)
```

Now create two points:
```{r}
pts <- data.frame(id = c("points_1", "points_2", "points_1", "points_2"), 
                  x = c(0, 0, 1, 1),
                  y = c(0, 1, 1, 0))

# Convert coordinates to points and then to simple features
pts <- pts %>%
  st_as_sf(coords = c("x", "y"))
```

Create circle segments:
```{r}
cs <- c(0.5, 0.35, 0.2)

bfs <- rbind(pts %>% 
               mutate(r = cs[1], 
                      geometry = pts %>%
                        st_buffer(dist = r) %>% 
                        pull(geometry)),
             pts %>% 
               mutate(r = cs[2], 
                      geometry = pts %>%
                        st_buffer(dist = r) %>% 
                        pull(geometry)),
             pts %>% 
               mutate(r = cs[3], 
                      geometry = pts %>%
                        st_buffer(dist = r) %>% 
                        pull(geometry)))
```

```{r}
bfs_1 <- bfs %>%
  filter(id == "points_1") %>%
  st_intersection(st_geometry(tile))

bfs_2 <- bfs %>%
  filter(id == "points_2") %>%
  st_intersection(st_geometry(tile))
```

Make tiles:
```{r}
tile_1 <- bfs_1 %>%
  transmute(c = case_when(r == cs[1] ~ 1,
                          r == cs[2] ~ 2,
                          r == cs[3] ~ 3))

tile_2 <- bfs_2 %>%
  transmute(c = case_when(r == cs[1] ~ 1,
                          r == cs[2] ~ 2,
                          r == cs[3] ~ 3))
```

Translate so that the origin is at the center of the tile:
```{r}
tile_1 <- tile_1 %>%
  mutate(geometry = st_geometry(tile_1) + c(-0.5, -0.5))

tile_2 <- tile_2 %>%
  mutate(geometry = st_geometry(tile_2) + c(-0.5, -0.5))

tiles <- rbind(data.frame(tile_1, tile = 1),
               data.frame(tile_2, tile = 2))
```

```{r}
# Create grid for placing tiles
df <- data.frame(expand.grid(x = seq(1, 8, 1),
                             y = seq(1, 12, 1)))

# Create container for mosaic
container <- matrix(c(min(df$x) - 0.5, min(df$y) - 0.5, 
                      min(df$x) - 0.5, max(df$y) + 0.5, 
                      max(df$x) + 0.5, max(df$y) + 0.5,  
                      max(df$x) + 0.5, min(df$y) - 0.5,
                      min(df$x) - 0.5, min(df$y) - 0.5),
                    ncol = 2,
                    byrow = TRUE)

# Convert coordinates of container to polygons and then to simple features
container <- data.frame(id = 1,
                        r = NA,
                        geometry = st_polygon(list(container)) %>% 
                          st_sfc()) %>% 
  st_as_sf()

mosaic <- data.frame()

for(i in 1:nrow(df)){
  mosaic <- rbind(mosaic,
                  tiles %>%
                    filter(tile == sample.int(2, 1)) %>%
                    mutate(geometry = geometry + c(df[i, 1], df[i, 2])) %>%
                    st_as_sf())
}

ggplot() +
  geom_sf(data = container) +
  geom_sf(data = mosaic,
          aes(fill = factor(c)),
          color = NA) + 
  theme_void()
```

Make pretty:
```{r}
# Create grid for placing tiles
df <- data.frame(expand.grid(x = seq(1, 8, 1),
                             y = seq(1, 12, 1)))

# Create container for mosaic
container <- matrix(c(min(df$x) - 0.5, min(df$y) - 0.5, 
                      min(df$x) - 0.5, max(df$y) + 0.5, 
                      max(df$x) + 0.5, max(df$y) + 0.5,  
                      max(df$x) + 0.5, min(df$y) - 0.5,
                      min(df$x) - 0.5, min(df$y) - 0.5),
                    ncol = 2,
                    byrow = TRUE)

# Convert coordinates of container to polygons and then to simple features
container <- data.frame(id = 1,
                        r = NA,
                        geometry = st_polygon(list(container)) %>% 
                          st_sfc()) %>% 
  st_as_sf()

mosaic <- data.frame()

for(i in 1:nrow(df)){
  mosaic <- rbind(mosaic,
                  tiles %>%
                    filter(tile == sample.int(2, 1)) %>%
                    mutate(geometry = geometry + c(df[i, 1], df[i, 2])) %>%
                    st_as_sf())
}

# Sample from color palette
col_palette <- mex.brewer("Alacena")
col_palette_1 <- col_palette[c(5, 6)]
col_palette_2 <- col_palette[-c(5, 6)]
col_palette_2 <- col_palette_2[sample.int(8, 3)] 


ggplot() +
  geom_sf(data = container,
          fill = col_palette_1[sample.int(2, 1)]) +
  geom_sf(data = mosaic,
          aes(fill = factor(c)),
          color = NA) + 
  scale_fill_manual(values = col_palette_2) +
  theme_void() +
  theme(legend.position = "none")
```

Inputs:
- A set of tiles
- Grid coordinates

Turn it into a function:
```{r}
st_truchet <- function(t, xlim = c(1, 8), ylim = c(1, 12)){
  # Create grid for placing tiles
  df <- data.frame(expand.grid(x = seq(xlim[1], xlim[2], 1),
                               y = seq(ylim[1], ylim[2], 1)))
  
  # Create container for mosaic
  container <- matrix(c(min(df$x) - 0.5, min(df$y) - 0.5, 
                        min(df$x) - 0.5, max(df$y) + 0.5, 
                        max(df$x) + 0.5, max(df$y) + 0.5,  
                        max(df$x) + 0.5, min(df$y) - 0.5,
                        min(df$x) - 0.5, min(df$y) - 0.5),
                      ncol = 2,
                      byrow = TRUE)
  
  # Convert coordinates of container to polygons and then to simple features
  container <- data.frame(id = 1,
                          r = NA,
                          geometry = st_polygon(list(container)) %>% 
                            st_sfc()) %>% 
    st_as_sf()
  
  mosaic <- data.frame()
  
  for(i in 1:nrow(df)){
    mosaic <- rbind(mosaic,
                    t %>%
                      filter(tile == sample.int(2, 1)) %>%
                      mutate(group = i,
                             geometry = geometry + c(df[i, 1], df[i, 2])) %>%
                      st_as_sf())
  }
  return(list(container = container, mosaic = mosaic))
}
```

Use function to create mosaic:
```{r}
mosaic <- st_truchet(tiles)

# Sample from color palette
col_palette <- mex.brewer("Revolucion")
col_palette_1 <- col_palette[c(5, 6)]
col_palette_2 <- col_palette[-c(5, 6)]
col_palette_2 <- col_palette_2[sample.int(8, 3)] 

# Plot
ggplot() +
  geom_sf(data = mosaic[["container"]],
          fill = col_palette_1[sample.int(2, 1)]) +
  geom_sf(data = mosaic[["mosaic"]],
          aes(fill = factor(c)),
          color = NA) + 
  scale_fill_manual(values = col_palette_2) +
  theme_void() +
  theme(legend.position = "none")
```

```{r}
# ggsave(filename = "truchet-atentado-1.png", 
#        width = 8, 
#        height = 12, 
#        units = "in")
```

## Change the tiles

Create circle segments:
```{r}
cs <- c(0.5)

bfs <- pts %>% 
  mutate(r = cs[1], 
         geometry = pts %>%
           st_buffer(dist = r) %>% 
           pull(geometry)) %>% 
  st_cast(to = "LINESTRING")
```

```{r}
bfs_1 <- bfs %>%
  filter(id == "points_1") %>%
  st_intersection(st_geometry(tile))

bfs_2 <- bfs %>%
  filter(id == "points_2") %>%
  st_intersection(st_geometry(tile))
```

Make tiles:
```{r}
tile_1 <- bfs_1

tile_2 <- bfs_2
```

Translate so that the origin is at the center of the tile:
```{r}
tile_1 <- tile_1 %>%
  mutate(geometry = st_geometry(tile_1) + c(-0.5, -0.5))

tile_2 <- tile_2 %>%
  mutate(geometry = st_geometry(tile_2) + c(-0.5, -0.5))

tiles <- rbind(data.frame(tile_1, tile = 1),
               data.frame(tile_2, tile = 2)) %>% 
  st_as_sf()
```

Use these new tiles to create mosaic:
```{r}
mosaic <- st_truchet(tiles)
container <- mosaic[["container"]]
mosaic <- mosaic[["mosaic"]]

# Sample from color palette
col_palette <- mex.brewer("Revolucion")
col_palette_1 <- col_palette[c(5, 6)]
col_palette_2 <- col_palette[-c(5, 6)]
#col_palette_2 <- col_palette_2[sample.int(8, 3)] 

# Plot
ggplot() +
  geom_sf(data = container,
          fill = col_palette[sample.int(10, 1)]) +
  geom_sf(data = mosaic,
          aes(color = group), #col_palette_2[sample.int(8, 1)],
          size = 6) + 
  scale_color_gradientn(colors = col_palette_2) +
  theme_void() + 
  theme(legend.position = "none")

# ggsave(filename = "truchet-revolucion-1.png", 
#        width = 8, 
#        height = 12, 
#        units = "in")
```

Animate process:
```{r}
# Plot
process_anim <- ggplot() +
  geom_sf(data = container,
          fill = col_palette[sample.int(10, 1)]) +
  geom_sf(data = mosaic,
          aes(color = group), #col_palette_2[sample.int(8, 1)],
          size = 2) + 
  scale_color_gradientn(colors = col_palette_2) +
  theme_void() + 
  theme(legend.position = "none") +
  transition_time(group) + 
  shadow_mark()

animate(process_anim,
        height = 3, 
        width = 2, 
        units = "in",
        res = 300)

anim_save("process_anim.gif")
```


Create different tiles:
```{r}

line_1 <- matrix(c(0, 1/10, 1/10, 3/10, 3/10, 1/2, 1/2,
                   1/2, 1/2, 7/10, 7/10, 9/10, 9/10, 1),
                 nrow = 7,
                 byrow = FALSE)

line_2 <- matrix(c(1/2, 1/2, 7/10, 7/10, 9/10, 9/10, 1,
                   0, 1/10, 1/10, 3/10, 3/10, 1/2, 1/2),
                 nrow = 7,
                 byrow = FALSE)

line_3 <- matrix(c(0, 1/10, 1/10, 3/10, 3/10, 1/2, 1/2,
                   1/2, 1/2, 3/10, 3/10, 1/10, 1/10, 0),
                 nrow = 7,
                 byrow = FALSE)

line_4 <- matrix(c(1/2, 1/2, 7/10, 7/10, 9/10, 9/10, 1,
                   1, 9/10, 9/10, 7/10, 7/10, 1/2, 1/2),
                 nrow = 7,
                 byrow = FALSE)

# Convert coordinates to lines and then to simple features
line_1 <- data.frame(id = 1,
                     r = NA,
                     geometry = st_linestring(line_1) %>% 
                   st_sfc()) %>% 
  st_as_sf()

line_2 <- data.frame(id = 2,
                     r = NA,
                     geometry = st_linestring(line_2) %>% 
                   st_sfc()) %>% 
  st_as_sf()

line_3 <- data.frame(id = 3,
                     r = NA,
                     geometry = st_linestring(line_3) %>% 
                   st_sfc()) %>% 
  st_as_sf()

line_4 <- data.frame(id = 4,
                     r = NA,
                     geometry = st_linestring(line_4) %>% 
                   st_sfc()) %>% 
  st_as_sf()
```

Make tiles:
```{r}
tile_1 <- rbind(line_1, line_2)

tile_2 <- rbind(line_3, line_4)
```

Translate so that the origin is at the center of the tile:
```{r}
tile_1 <- tile_1 %>%
  mutate(geometry = st_geometry(tile_1) + c(-0.5, -0.5))

tile_2 <- tile_2 %>%
  mutate(geometry = st_geometry(tile_2) + c(-0.5, -0.5))

tiles <- rbind(data.frame(tile_1, tile = 1),
               data.frame(tile_2, tile = 2)) %>%
  st_as_sf()
```

Use these new tiles to create mosaic:
```{r}
mosaic <- st_truchet(tiles)
container <- mosaic[["container"]]
mosaic <- mosaic[["mosaic"]]

# Sample from color palette
col_palette <- mex.brewer("Revolucion")
col_palette_1 <- col_palette[c(5, 6)]
col_pal1ette_2 <- col_palette[-c(5, 6)]
#col_palette_2 <- col_palette_2[sample.int(8, 3)] 

# Plot
ggplot() +
  geom_sf(data = container,
          fill = col_palette[sample.int(10, 1)]) +
  geom_sf(data = mosaic,
          aes(color = group), #col_palette_2[sample.int(8, 1)],
          size = 6) + 
  scale_color_gradientn(colors = col_palette) +
  theme_void() + 
  theme(legend.position = "none")

# ggsave(filename = "truchet-revolucion-blocks-1.png", 
#        width = 8, 
#        height = 12, 
#        units = "in")
```

Change palette
```{r}
mosaic <- st_truchet(tiles)
container <- mosaic[["container"]]
mosaic <- mosaic[["mosaic"]]

# Sample from color palette
col_palette <- mex.brewer("Atentado")
col_palette_1 <- col_palette[c(5, 6)]
col_pal1ette_2 <- col_palette[-c(5, 6)]
#col_palette_2 <- col_palette_2[sample.int(8, 3)] 

# Plot
ggplot() +
  geom_sf(data = container,
          fill = col_palette[sample.int(10, 1)]) +
  geom_sf(data = mosaic,
          aes(color = group), #col_palette_2[sample.int(8, 1)],
          size = 6) + 
  scale_color_gradientn(colors = col_palette) +
  theme_void() + 
  theme(legend.position = "none")

#ggsave(filename = "truchet-atentado-blocks-1.png", 
#       width = 8, 
#       height = 12, 
#       units = "in")
```

## Refinements

### Union of lines?

Create circle segments:
```{r}
cs <- c(0.5)

bfs <- pts %>% 
  mutate(r = cs[1], 
         geometry = pts %>%
           st_buffer(dist = r) %>% 
           pull(geometry)) %>% 
  st_cast(to = "LINESTRING")
```

```{r}
bfs_1 <- bfs %>%
  filter(id == "points_1") %>%
  st_intersection(st_geometry(tile))

bfs_2 <- bfs %>%
  filter(id == "points_2") %>%
  st_intersection(st_geometry(tile))
```

Make tiles:
```{r}
tile_1 <- bfs_1

tile_2 <- bfs_2
```

Translate so that the origin is at the center of the tile:
```{r}
tile_1 <- tile_1 %>%
  mutate(geometry = st_geometry(tile_1) + c(-0.5, -0.5))

tile_2 <- tile_2 %>%
  mutate(geometry = st_geometry(tile_2) + c(-0.5, -0.5))

tiles <- rbind(data.frame(tile_1, tile = 1),
               data.frame(tile_2, tile = 2)) %>% 
  st_as_sf()
```


```{r}
mosaic <- st_truchet(tiles)
container <- mosaic[["container"]]
mosaic <- mosaic[["mosaic"]]
```

Union:
```{r}
mosaic_buffer <- st_union(mosaic)
```

```{r}
mosaic_buffer <- rbind(data.frame(group = 1, 
                           st_buffer(mosaic_buffer, dist = c(0.2))) %>% 
                  st_as_sf(),
                data.frame(group = 2, 
                           st_buffer(mosaic_buffer, dist = c(0.1))) %>% 
                  st_as_sf(),
                data.frame(group = 3, 
                           st_buffer(mosaic_buffer, dist = c(0.05))) %>% 
                  st_as_sf())

```


```{r}
col_palette <- mex.brewer("Atentado")
col_palette_1 <- col_palette[c(5, 6)]
col_pal1ette_2 <- col_palette[-c(5, 6)]
#col_palette_2 <- col_palette_2[sample.int(8, 3)] 

# Plot
ggplot() +
  geom_sf(data = container,
          fill = col_palette[sample.int(10, 1)]) +
  geom_sf(data = mosaic_buffer,
          aes(fill = factor(group))) + 
  scale_fill_manual(values = c(col_palette[sample.int(10, 1)], 
                               "white", 
                               col_palette[sample.int(10, 1)])) +
  theme_void() + 
  theme(legend.position = "none")

ggsave(filename = "truchet-atentado-buffered-1.png", 
       width = 8, 
       height = 12, 
       units = "in")
```

```{r}
col_palette <- mex.brewer("Revolucion")
col_palette_1 <- col_palette[c(5, 6)]
col_pal1ette_2 <- col_palette[-c(5, 6)]
#col_palette_2 <- col_palette_2[sample.int(8, 3)] 

# Plot
ggplot() +
  geom_sf(data = container,
          fill = col_palette[sample.int(10, 1)]) +
  geom_sf(data = mosaic_buffer,
          aes(fill = factor(group))) + 
  scale_fill_manual(values = c(col_palette[sample.int(10, 1)], 
                               "white", 
                               col_palette[sample.int(10, 1)])) +
  theme_void() + 
  theme(legend.position = "none")

ggsave(filename = "truchet-revolucion-buffered-1.png", 
       width = 8, 
       height = 12, 
       units = "in")
```



```{r}
col_palette <- mex.brewer("Frida")
col_palette_1 <- col_palette[c(5, 6)]
col_pal1ette_2 <- col_palette[-c(5, 6)]
#col_palette_2 <- col_palette_2[sample.int(8, 3)] 

# Plot
ggplot() +
  geom_sf(data = container,
          fill = col_palette[sample.int(10, 1)]) +
  geom_sf(data = mosaic_buffer,
          aes(fill = factor(group))) + 
  scale_fill_manual(values = c(col_palette[sample.int(10, 1)], 
                               "white", 
                               col_palette[sample.int(10, 1)])) +
  theme_void() + 
  theme(legend.position = "none")

ggsave(filename = "truchet-frida-buffered-1.png", 
       width = 8, 
       height = 12, 
       units = "in")
```

```{r}
col_palette <- mex.brewer("Aurora")
col_palette_1 <- col_palette[c(5, 6)]
col_pal1ette_2 <- col_palette[-c(5, 6)]
#col_palette_2 <- col_palette_2[sample.int(8, 3)] 

# Plot
ggplot() +
  geom_sf(data = container,
          fill = col_palette[sample.int(10, 1)]) +
  geom_sf(data = mosaic_buffer,
          aes(fill = factor(group))) + 
  scale_fill_manual(values = c(col_palette[sample.int(10, 1)], 
                               "white", 
                               col_palette[sample.int(10, 1)])) +
  theme_void() + 
  theme(legend.position = "none")

ggsave(filename = "truchet-aurora-buffered-1.png", 
       width = 8, 
       height = 12, 
       units = "in")
```

```{r}
col_palette <- mex.brewer("Alacena")
col_palette_1 <- col_palette[c(5, 6)]
col_pal1ette_2 <- col_palette[-c(5, 6)]
#col_palette_2 <- col_palette_2[sample.int(8, 3)] 

# Plot
ggplot() +
  geom_sf(data = container,
          fill = col_palette[sample.int(10, 1)]) +
  geom_sf(data = mosaic_buffer,
          aes(fill = factor(group))) + 
  scale_fill_manual(values = c(col_palette[sample.int(10, 1)], 
                               "white", 
                               col_palette[sample.int(10, 1)])) +
  theme_void() + 
  theme(legend.position = "none")

ggsave(filename = "truchet-alacena-buffered-1.png", 
       width = 8, 
       height = 12, 
       units = "in")
```






