---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Abstract vegatation

<!-- badges: start -->
<!-- badges: end -->

Too busy today writing to try to create abstract vegetation from a scratch. Thankfully, [Pierre Casadebaig](https://github.com/picasa) has generously made his code public, and I have been very curious to explore his asemic characters and vegetation-like plots. So this is a great opportunity for it!

As explained [here](https://github.com/picasa/generative_examples/blob/master/R/sequence_collatz.rmd#L25), vegetation-like shapes can be obtained by defining a curve that maps a sequence of integers to segment lengths, changing the angle between segments by some pre-determined amount. Nodes are made of multiple curves, and stems are made of multiple nodes. 

This example uses Casadebaig's package [{generate}](https://github.com/picasa/generate):
```{r setup}
library(ggforce)
library(MexBrewer)
library(tidyverse)
# functions
# remotes::install_github("picasa/generate")
library(generate)
```

Here I create a few figures with a single node and dense polygons. This is basically Casadebaig's example with just some minor changes in the inputs. Instead of using the `render_node()` function, I extract the rendering commands to have more control on the aspect of the plot. I will also try different color palettes from my package [{MexBrewer}]().

## Atentado

```{r plot-dense-atentado}
# plot a single node with dense polygons
p_seed = 12
p_node = 300
p_imax = 100
p_lmax = 3000
p_angle = 60
p_shift = 4
p_width = c(0, 10)
p_render = "spline"

# seeds 4, 8, 11
data_dense <- gen_node(n = p_node, 
                       imax = p_imax, 
                       lmax = p_lmax,
                       amin = -p_angle, 
                       amax = p_angle, 
                       shift = p_shift, 
                       width = p_width, 
                       seed = p_seed, 
                       method = p_render)

# Create random variable to add colors
col_table <- data.frame(id = 1:max(data_dense$id)) %>%
  mutate(color = runif(max(id)))

# Choose color palette
col_palette <- MexBrewer::mex.brewer("Atentado")

# Join to data table
data_dense_plus <- data_dense %>%
  left_join(col_table,
            by = c("id"))

data_dense_plus %>%
  ggplot(aes(x,y, group = id)) +
  geom_shape(aes(fill = color),
             color="black",
             size = 0.5, 
             radius = grid::unit(0, 'pt')) +
  coord_fixed(xlim = c(-100, 100),
                       ylim = c(180,460)) +
  scale_fill_gradientn(colors = col_palette) +
  theme_void() +
  theme(legend.position = "none",
        plot.margin = rep(grid::unit(10, "pt"), 4))
```

Save plot:
```{r}
ggsave(file = "abstract-vegetation-atentado.png",
  width = 7, 
  height = 7,
  dpi = 300, 
  scale = 1,
  units="in")
```

## Revolucion

```{r plot-dense-revolucion}
# plot a single node with dense polygons
p_seed = 53
p_node = 300
p_imax = 100
p_lmax = 3000
p_angle = 35
p_shift = 4
p_width = c(0, 10)
p_render = "spline"

# seeds 4, 8, 11
data_dense <- gen_node(n = p_node, 
                       imax = p_imax, 
                       lmax = p_lmax,
                       amin = -p_angle, 
                       amax = p_angle, 
                       shift = p_shift, 
                       width = p_width, 
                       seed = p_seed, 
                       method = p_render)

# Create random variable to add colors
col_table <- data.frame(id = 1:max(data_dense$id)) %>%
  mutate(color = runif(max(id)))

# Choose color palette
col_palette <- MexBrewer::mex.brewer("Revolucion")

# Join to data table
data_dense_plus <- data_dense %>%
  left_join(col_table,
            by = c("id"))

data_dense_plus %>%
  ggplot(aes(x,y, group = id)) +
  geom_shape(aes(fill = color),
             color="black",
             size = 0.5, 
             radius = grid::unit(0, 'pt')) +
  coord_fixed(xlim = c(-100, 100),
                       ylim = c(180,460)) +
  scale_fill_gradientn(colors = col_palette) +
  theme_void() +
  theme(legend.position = "none",
        plot.margin = rep(grid::unit(10, "pt"), 4))
```

Save plot:
```{r}
ggsave(file = "abstract-vegetation-revolucion.png",
  width = 7, 
  height = 7,
  dpi = 300, 
  scale = 1,
  units="in")
```


## Frida

```{r plot-dense-frida}
# plot a single node with dense polygons
p_seed = 8
p_node = 300
p_imax = 100
p_lmax = 3000
p_angle = 70
p_shift = 4
p_width = c(0, 10)
p_render = "spline"

# seeds 4, 8, 11
data_dense <- gen_node(n = p_node, 
                       imax = p_imax, 
                       lmax = p_lmax,
                       amin = -p_angle, 
                       amax = p_angle, 
                       shift = p_shift, 
                       width = p_width, 
                       seed = p_seed, 
                       method = p_render)

# Create random variable to add colors
col_table <- data.frame(id = 1:max(data_dense$id)) %>%
  mutate(color = runif(max(id)))

# Choose color palette
col_palette <- MexBrewer::mex.brewer("Frida")

# Join to data table
data_dense_plus <- data_dense %>%
  left_join(col_table,
            by = c("id"))

data_dense_plus %>%
  ggplot(aes(x,y, group = id)) +
  geom_shape(aes(fill = color),
             color="black",
             size = 0.5, 
             radius = grid::unit(0, 'pt')) +
  coord_fixed(xlim = c(-100, 100),
                       ylim = c(180,460)) +
  scale_fill_gradientn(colors = col_palette) +
  theme_void() +
  theme(legend.position = "none",
        plot.margin = rep(grid::unit(10, "pt"), 4))
```

Save plot:
```{r}
ggsave(file = "abstract-vegetation-frida.png",
  width = 7, 
  height = 7,
  dpi = 300, 
  scale = 1,
  units="in")
```

## Ronda

```{r plot-dense-ronda}
# plot a single node with dense polygons
p_seed = 30
p_node = 300
p_imax = 100
p_lmax = 3000
p_angle = 45
p_shift = 4
p_width = c(0, 10)
p_render = "spline"

# seeds 4, 8, 11
data_dense <- gen_node(n = p_node, 
                       imax = p_imax, 
                       lmax = p_lmax,
                       amin = -p_angle, 
                       amax = p_angle, 
                       shift = p_shift, 
                       width = p_width, 
                       seed = p_seed, 
                       method = p_render)

# Create random variable to add colors
col_table <- data.frame(id = 1:max(data_dense$id)) %>%
  mutate(color = runif(max(id)))

# Choose color palette
col_palette <- MexBrewer::mex.brewer("Ronda")

# Join to data table
data_dense_plus <- data_dense %>%
  left_join(col_table,
            by = c("id"))

data_dense_plus %>%
  ggplot(aes(x,y, group = id)) +
  geom_shape(aes(fill = color),
             color="black",
             size = 0.5, 
             radius = grid::unit(0, 'pt')) +
  coord_fixed(xlim = c(-100, 100),
                       ylim = c(180,460)) +
  scale_fill_gradientn(colors = col_palette) +
  theme_void() +
  theme(legend.position = "none",
        plot.margin = rep(grid::unit(10, "pt"), 4))
```

Save plot:
```{r}
ggsave(file = "abstract-vegetation-ronda.png",
  width = 7, 
  height = 7,
  dpi = 300, 
  scale = 1,
  units="in")
```

## Tierra

```{r plot-dense-tierra}
# plot a single node with dense polygons
p_seed = 3
p_node = 300
p_imax = 100
p_lmax = 3000
p_angle = 20
p_shift = 4
p_width = c(0, 10)
p_render = "spline"

# seeds 4, 8, 11
data_dense <- gen_node(n = p_node, 
                       imax = p_imax, 
                       lmax = p_lmax,
                       amin = -p_angle, 
                       amax = p_angle, 
                       shift = p_shift, 
                       width = p_width, 
                       seed = p_seed, 
                       method = p_render)

# Create random variable to add colors
col_table <- data.frame(id = 1:max(data_dense$id)) %>%
  mutate(color = runif(max(id)))

# Choose color palette
col_palette <- MexBrewer::mex.brewer("Tierra")

# Join to data table
data_dense_plus <- data_dense %>%
  left_join(col_table,
            by = c("id"))

data_dense_plus %>%
  ggplot(aes(x,y, group = id)) +
  geom_shape(aes(fill = color),
             color="black",
             size = 0.5, 
             radius = grid::unit(0, 'pt')) +
  coord_fixed(xlim = c(-100, 100),
                       ylim = c(180,460)) +
  scale_fill_gradientn(colors = col_palette) +
  theme_void() +
  theme(legend.position = "none",
        plot.margin = rep(grid::unit(10, "pt"), 4))
```

Save plot:
```{r}
ggsave(file = "abstract-vegetation-tierra.png",
  width = 7, 
  height = 7,
  dpi = 300, 
  scale = 1,
  units="in")
```
