---
output:
  github_document:
    pandoc_args: --webtex
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE
)
```

# Three colors

<!-- badges: start -->
<!-- badges: end -->

I will experiment with some outlines given by selective hatching.

```{r load-packages, cache = FALSE, warning=FALSE, message=FALSE}
library(MexBrewer)
library(sf)
library(tidyverse)
```

## Create some Truchet tiles

Create a one-by-one tile:
```{r}
tile <- matrix(c(0, 0, 
                 0, 1, 
                 1, 1,  
                 1, 0,
                 0, 0),
               ncol = 2,
               byrow = TRUE)

# Convert coordinates to polygons and then to simple features
tile <- data.frame(id = 1,
                   r = NA,
                   geometry = st_polygon(list(tile)) %>% 
                     st_sfc()) %>% 
  st_as_sf()
```

Plot tile:
```{r}
ggplot() +
  geom_sf(data =  tile)
```

Now create two points:
```{r}
pts <- data.frame(id = c("points_1", "points_2", "points_1", "points_2"), 
                  x = c(0, 0, 1, 1),
                  y = c(0, 1, 1, 0))

# Convert coordinates to points and then to simple features
pts <- pts %>%
  st_as_sf(coords = c("x", "y"))
```

Create circle segments:
```{r}
cs <- c(0.5)

bfs <- pts %>% 
  mutate(r = cs[1], 
         geometry = pts %>%
           st_buffer(dist = r) %>% 
           pull(geometry)) %>% 
  st_cast(to = "LINESTRING")
```

```{r}
bfs_1 <- bfs %>%
  filter(id == "points_1") %>%
  st_intersection(st_geometry(tile))

bfs_2 <- bfs %>%
  filter(id == "points_2") %>%
  st_intersection(st_geometry(tile))
```

Make tiles:
```{r}
tile_1 <- bfs_1

tile_2 <- bfs_2
```

Translate so that the origin is at the center of the tile:
```{r}
tile_1 <- tile_1 %>%
  mutate(geometry = st_geometry(tile_1) + c(-0.5, -0.5))

tile_2 <- tile_2 %>%
  mutate(geometry = st_geometry(tile_2) + c(-0.5, -0.5))

tiles <- rbind(data.frame(tile_1, tile = 1),
               data.frame(tile_2, tile = 2)) %>% 
  st_as_sf()
```

Function for Truchet tiles:
```{r}
st_truchet <- function(t, xlim = c(1, 8), ylim = c(1, 12)){
  # Create grid for placing tiles
  df <- data.frame(expand.grid(x = seq(xlim[1], xlim[2], 1),
                               y = seq(ylim[1], ylim[2], 1)))
  
  # Create container for mosaic
  container <- matrix(c(min(df$x) - 0.5, min(df$y) - 0.5, 
                        min(df$x) - 0.5, max(df$y) + 0.5, 
                        max(df$x) + 0.5, max(df$y) + 0.5,  
                        max(df$x) + 0.5, min(df$y) - 0.5,
                        min(df$x) - 0.5, min(df$y) - 0.5),
                      ncol = 2,
                      byrow = TRUE)
  
  # Convert coordinates of container to polygons and then to simple features
  container <- data.frame(id = 1,
                          r = NA,
                          geometry = st_polygon(list(container)) %>% 
                            st_sfc()) %>% 
    st_as_sf()
  
  mosaic <- data.frame()
  
  for(i in 1:nrow(df)){
    mosaic <- rbind(mosaic,
                    t %>%
                      filter(tile == sample.int(2, 1)) %>%
                      mutate(group = i,
                             geometry = geometry + c(df[i, 1], df[i, 2])) %>%
                      st_as_sf())
  }
  return(list(container = container, mosaic = mosaic))
}
```


```{r}
mosaic <- st_truchet(tiles)
container <- mosaic[["container"]]
mosaic <- mosaic[["mosaic"]]
```

Union:
```{r}
mosaic_buffer <- st_union(mosaic)
```

```{r}
mosaic_buffer <- rbind(data.frame(group = 1, 
                                  st_buffer(mosaic_buffer, dist = c(0.2))) %>% 
                         st_as_sf(),
                       data.frame(group = 2, 
                                  st_buffer(mosaic_buffer, dist = c(0.1))) %>% 
                         st_as_sf(),
                       data.frame(group = 3, 
                                  st_buffer(mosaic_buffer, dist = c(0.05))) %>% 
                         st_as_sf())

```


```{r}
col_palette <- mex.brewer("Atentado")
col_palette_1 <- col_palette[c(5, 6)]
col_pal1ette_2 <- col_palette[-c(5, 6)]
#col_palette_2 <- col_palette_2[sample.int(8, 3)] 

# Plot
ggplot() +
  geom_sf(data = container) +
  geom_sf(data = mosaic_buffer,
          aes(fill = factor(group)))
```

Create hatching patterns:
```{r}
# Number of points for hatching pattern
n_hatch <- 7500

# Create vertical hatching pattern
df_hatch_1 <- data.frame(x = runif(n_hatch, 
                                   min = st_bbox(container)[1], 
                                   max = st_bbox(container)[3]),
                         y = runif(n_hatch,
                                   min = st_bbox(container)[2],
                                   max = st_bbox(container)[4])) %>%
  # Calculate endpoints for the line segments that will produce the hatching
  mutate(xend = x,
         yend = y - runif(n(), 
                          min = 0.75, 
                          max = runif(n(), 
                                      min = 1,
                                      max = 1.5)))
df_hatch_1_coords <- df_hatch_1 %>% 
  select(x, 
         y)

# Create horizontal hatching pattern
df_hatch_2 <- data.frame(x = runif(n_hatch, 
                                   min = st_bbox(container)[1], 
                                   max = st_bbox(container)[3]),
                         y = runif(n_hatch,
                                   min = st_bbox(container)[2],
                                   max = st_bbox(container)[4])) %>%
  # Calculate endpoints for the line segments that will produce the hatching
  mutate(xend = x + runif(n(), 
                          min = 0.75, 
                          max = runif(n(), 
                                      min = 1,
                                      max = 1.5)),
         yend = y)

df_hatch_2_coords <- df_hatch_2 %>% 
  select(x, 
         y)

# Create diagonal hatching pattern
df_hatch_3 <- data.frame(x = runif(n_hatch, 
                                   min = st_bbox(container)[1], 
                                   max = st_bbox(container)[3]),
                         y = runif(n_hatch,
                                   min = st_bbox(container)[2],
                                   max = st_bbox(container)[4])) %>%
  # Calculate endpoints for the line segments that will produce the hatching
  mutate(l = runif(n(), 
                   min = 0.75, 
                   max = runif(n(), 
                               min = 1,
                               max = 1.5)),
         xend = x + l,
         yend = y - l)

df_hatch_3_coords <- df_hatch_3 %>% 
  select(x, 
         y)

# Create opposite hatching pattern
df_hatch_4 <- data.frame(x = runif(n_hatch, 
                                   min = st_bbox(container)[1], 
                                   max = st_bbox(container)[3]),
                         y = runif(n_hatch,
                                   min = st_bbox(container)[2],
                                   max = st_bbox(container)[4])) %>%
  # Calculate endpoints for the line segments that will produce the hatching
  mutate(l = runif(n(), 
                   min = 0.75, 
                   max = runif(n(), 
                               min = 1,
                               max = 1.5)),
         xend = x + l,
         yend = y + l)

df_hatch_4_coords <- df_hatch_4 %>% 
  select(x, 
         y)
```

Plot these hatching patterns:
```{r}
ggplot() +
  geom_segment(data = df_hatch_1 %>%
                 filter(xend > 1 & xend < 8, 
                        yend > 1 & yend < 12),
               aes(x = x, 
                   y = y,
                   xend = xend,
                   yend = yend),
               #alpha = (y/30)^4),
               size = 0.1) +
  geom_segment(data = df_hatch_2 %>%
                 filter(xend > 1 & xend < 8, 
                        yend > 1 & yend < 12),
               aes(x = x, 
                   y = y,
                   xend = xend,
                   yend = yend),
               #alpha = (y/30)^4),
               size = 0.1) +
  geom_segment(data = df_hatch_3 %>%
                 filter(xend > 1 & xend < 8, 
                        yend > 1 & yend < 12),
               aes(x = x, 
                   y = y,
                   xend = xend,
                   yend = yend),
               #alpha = (y/30)^4),
               size = 0.1) +
  geom_segment(data = df_hatch_4 %>%
                 filter(xend > 1 & xend < 8, 
                        yend > 1 & yend < 12),
               aes(x = x, 
                   y = y,
                   xend = xend,
                   yend = yend),
               #alpha = (y/30)^4),
               size = 0.1) +
  coord_equal()
```

Make a function to convert hatching to sf:
```{r}
make_line <- function(x, y, xend, yend) {
  st_linestring(matrix(c(x, xend, y, yend), 2, 2))
}
```

Convert to sf:
```{r}

df_hatch_1 <- df_hatch_1 %>%
  select(x, y, xend, yend) %>% 
  pmap(make_line) %>%
  st_as_sfc()

df_hatch_2 <- df_hatch_2 %>%
  select(x, y, xend, yend) %>% 
  pmap(make_line) %>%
  st_as_sfc()

df_hatch_3 <- df_hatch_3 %>%
  select(x, y, xend, yend) %>% 
  pmap(make_line) %>%
  st_as_sfc()

df_hatch_4 <- df_hatch_4 %>%
  select(x, y, xend, yend) %>% 
  pmap(make_line) %>%
  st_as_sfc()
```

Crop the hatching patterns using the container:
```{r}
df_hatch_1 <- df_hatch_1_coords %>% 
  mutate(geometry = st_geometry(df_hatch_1)) %>%
  st_as_sf() %>%
  st_crop(container)

df_hatch_2 <- df_hatch_1_coords %>% 
  mutate(geometry = st_geometry(df_hatch_2)) %>%
  st_as_sf() %>%
  st_crop(container)

df_hatch_3 <- df_hatch_3_coords %>% 
  mutate(geometry = st_geometry(df_hatch_3)) %>%
  st_as_sf() %>%
  st_crop(container)

df_hatch_4 <- df_hatch_4_coords %>% 
  mutate(geometry = st_geometry(df_hatch_4)) %>%
  st_as_sf() %>%
  st_crop(container)
```

Plot:
```{r}
ggplot() +
  geom_sf(data = df_hatch_1) +
  geom_sf(data = df_hatch_2) +
  geom_sf(data = df_hatch_3) +
  geom_sf(data = df_hatch_4) +
  geom_sf(data = container,
          color = "blue",
          fill = NA)
```

Use the truchet tiles to crop pattern 2:
```{r}
df_hatch_1_cropped <- df_hatch_1 %>%
  st_intersection(mosaic_buffer %>%
                    filter(group == 1))

df_hatch_2_cropped <- df_hatch_2 %>%
  st_intersection(mosaic_buffer %>%
                    filter(group == 1))

df_hatch_3_cropped <- df_hatch_3 %>%
  st_difference(mosaic_buffer %>%
                  filter(group == 1))

df_hatch_4_cropped <- df_hatch_4 %>%
  st_difference(mosaic_buffer %>%
                  filter(group == 1))
```

Plot the cropped pattern:
```{r}
ggplot() +
  geom_sf(data = df_hatch_1_cropped) +
  geom_sf(data = df_hatch_2_cropped) +
  geom_sf(data = df_hatch_3_cropped) +
  geom_sf(data = df_hatch_4_cropped) +
  theme_void()
```

Make pretty.

### Frida

```{r}
col_palette <- mex.brewer("Frida")
col_1 <- col_palette[sample.int(10, 1)]
col_2 <- col_palette[sample.int(10, 1)]

ggplot()  +
  geom_sf(data = df_hatch_3_cropped,
          #aes(alpha = ((st_bbox(container)[3] - x) * (st_bbox(container)[4] - y))),
          color = col_1,
          size = 0.25) +
  geom_sf(data = df_hatch_4_cropped,
          #aes(alpha = ((st_bbox(container)[3] - x) * (st_bbox(container)[4] - y))),
          color = col_1,
          size = 0.25) +
  geom_sf(data = df_hatch_1_cropped,
          #alpha = x * y
          color = col_2,
          size = 0.25) +
  geom_sf(data = df_hatch_2_cropped,
          #aes(alpha = x * y),
          color = col_2,
          size = 0.25) +
  scale_color_gradientn(colors = col_palette) +
  theme_void() +
  theme(legend.position = "none")

ggsave(filename = "two-colors-frida.png", 
       width = 4, 
       height = 6, 
       units = "in")
```
### Aurora

```{r}
col_palette <- mex.brewer("Aurora")
col_1 <- col_palette[sample.int(10, 1)]
col_2 <- col_palette[sample.int(10, 1)]

ggplot()  +
  geom_sf(data = df_hatch_3_cropped,
          #aes(alpha = ((st_bbox(container)[3] - x) * (st_bbox(container)[4] - y))),
          color = col_1,
          size = 0.25) +
  geom_sf(data = df_hatch_4_cropped,
          #aes(alpha = ((st_bbox(container)[3] - x) * (st_bbox(container)[4] - y))),
          color = col_1,
          size = 0.25) +
  geom_sf(data = df_hatch_1_cropped,
          #alpha = x * y
          color = col_2,
          size = 0.25) +
  geom_sf(data = df_hatch_2_cropped,
          #aes(alpha = x * y),
          color = col_2,
          size = 0.25) +
  scale_color_gradientn(colors = col_palette) +
  theme_void() +
  theme(legend.position = "none")

ggsave(filename = "two-colors-aurora.png", 
       width = 4, 
       height = 6, 
       units = "in")
```

### Atentado

```{r}
col_palette <- mex.brewer("Atentado")
col_1 <- col_palette[sample.int(10, 1)]
col_2 <- col_palette[sample.int(10, 1)]

ggplot()  +
  geom_sf(data = df_hatch_3_cropped,
          #aes(alpha = ((st_bbox(container)[3] - x) * (st_bbox(container)[4] - y))),
          color = col_1,
          size = 0.25) +
  geom_sf(data = df_hatch_4_cropped,
          #aes(alpha = ((st_bbox(container)[3] - x) * (st_bbox(container)[4] - y))),
          color = col_1,
          size = 0.25) +
  geom_sf(data = df_hatch_1_cropped,
          #alpha = x * y
          color = col_2,
          size = 0.25) +
  geom_sf(data = df_hatch_2_cropped,
          #aes(alpha = x * y),
          color = col_2,
          size = 0.25) +
  scale_color_gradientn(colors = col_palette) +
  theme_void() +
  theme(legend.position = "none")

ggsave(filename = "two-colors-atentado.png", 
       width = 4, 
       height = 6, 
       units = "in")
```

### Revolucion

```{r}
col_palette <- mex.brewer("Revolucion")
col_1 <- col_palette[sample.int(10, 1)]
col_2 <- col_palette[sample.int(10, 1)]

ggplot()  +
  geom_sf(data = df_hatch_3_cropped,
          #aes(alpha = ((st_bbox(container)[3] - x) * (st_bbox(container)[4] - y))),
          color = col_1,
          size = 0.25) +
  geom_sf(data = df_hatch_4_cropped,
          #aes(alpha = ((st_bbox(container)[3] - x) * (st_bbox(container)[4] - y))),
          color = col_1,
          size = 0.25) +
  geom_sf(data = df_hatch_1_cropped,
          #alpha = x * y
          color = col_2,
          size = 0.25) +
  geom_sf(data = df_hatch_2_cropped,
          #aes(alpha = x * y),
          color = col_2,
          size = 0.25) +
  scale_color_gradientn(colors = col_palette) +
  theme_void() +
  theme(legend.position = "none")

ggsave(filename = "two-colors-revolucion.png", 
       width = 4, 
       height = 6, 
       units = "in")
```

## Try points

Random points thinned by position:
```{r}
n_points <- 200000

df_points <- data.frame(x = runif(n_points, 
                                  min = st_bbox(container)[1], 
                                  max = st_bbox(container)[3]),
                        y = runif(n_points,
                                  min = st_bbox(container)[2],
                                  max = st_bbox(container)[4]))
```

Thin:
```{r eval = FALSE}
ggplot() +
  geom_point(data = df_points %>% 
               mutate(p = ifelse(rbinom(n(), 
                                        1, 
                                        p =((st_bbox(container)[4]) - y)/st_bbox(container)[4]) == 1, 
                                 1, 
                                 0)) %>%
               filter(p == 1),
             aes(x, y),
             color = "brown") +
  geom_point(data = df_points %>% 
               mutate(p = ifelse(rbinom(n(), 
                                        1, 
                                        p =((st_bbox(container)[4]) - y)/st_bbox(container)[4]) == 1, 
                                 1, 
                                 0)) %>%
               filter(p == 0),
             aes(x, y),
             color = "yellow")
```

Convert to sf and crop:
```{r}
df_points_1 <- df_points %>%
  # Thin by position: probability of being selected is higher with larger y
  mutate(p = ifelse(rbinom(n(), 
                           1, 
                           p =((st_bbox(container)[4]) - y)/st_bbox(container)[4]) == 1, 
                    1, 
                    0)) %>%
  # Filter chosen
  filter(p == 1) %>%
  # Add a size variable for texture
  mutate(size = runif(n(), 0.1, 0.3)) %>%
  # Add a variable for color to add "grains": about p = 10% of dots are "grains"
  mutate(color = ifelse(rbinom(n(), 
                           1, 
                           p = 0.90),
                        2,
                        1)) %>%
  st_as_sf(coords = c("x", "y")) %>%
  st_intersection(mosaic_buffer %>%
                  filter(group == 1))

df_points_2 <- df_points %>%
  # Thin by position: probability of being selected is higher with larger y
  mutate(p = ifelse(rbinom(n(), 
                           1, 
                           p =((st_bbox(container)[4]) - y)/st_bbox(container)[4]) == 1, 
                    1, 
                    0)) %>%
  # Filter NOT chosen
  filter(p == 0) %>%
  # Add a size variable for texture
  mutate(size = runif(n(), 0.1, 0.3)) %>%
  # Add a variable for color to add "grains": about p = 10% of dots are "grains"
  mutate(color = ifelse(rbinom(n(), 
                           1, 
                           p = 0.90),
                        
                        3,
                        1)) %>%
  st_as_sf(coords = c("x", "y")) %>%
  st_difference(mosaic_buffer %>%
                  filter(group == 1))
```

Plot:
```{r eval = FALSE}
ggplot() +
  geom_sf(data = df_points_1)

ggplot() +
  geom_sf(data = df_points_2)
```

Make pretty:
```{r}
col_palette <- mex.brewer("Tierra")[2:5]
col_background <- mex.brewer("Tierra")[1]
col_1 <- col_palette[sample.int(5, 1)]
col_2 <- col_palette[sample.int(5, 1)]

ggplot() +
  geom_sf(data = container,
          color = NA,
          fill = col_background) +
  geom_sf(data = df_points_1,
          aes(size = size,
              color = factor(color))) +
  geom_sf(data = df_points_2,
          aes(size =  size,
              color = factor(color))) + 
  scale_color_manual(values = c("1" = "black", "2" = col_1, "3" = col_2)) +
  scale_size(range = c(0.01, 0.05)) +
  theme_void() +
  theme(legend.position = "none")

ggsave(filename = "sandcasted-frida.png", 
       width = 8, 
       height = 12, 
       units = "in")
```


```{r}
col_palette <- mex.brewer("Aurora")[2:5]
col_background <- mex.brewer("Aurora")[1]
col_1 <- col_palette[sample.int(5, 1)]
col_2 <- col_palette[sample.int(5, 1)]

ggplot() +
  geom_sf(data = container,
          color = NA,
          fill = col_background) +
  geom_sf(data = df_points_1,
          aes(size = size,
              color = factor(color))) +
  geom_sf(data = df_points_2,
          aes(size =  size,
              color = factor(color))) + 
  scale_color_manual(values = c("1" = "black", "2" = col_1, "3" = col_2)) +
  scale_size(range = c(0.01, 0.05)) +
  theme_void() +
  theme(legend.position = "none")

ggsave(filename = "sandcasted-aurora.png", 
       width = 8, 
       height = 12, 
       units = "in")
```

```{r}
col_palette <- mex.brewer("Alacena")[-c(5, 6)]
col_background <- mex.brewer("Alacena")[c(5, 6)]
col_background <- col_background[sample.int(2, 1)]
col_1 <- col_palette[sample.int(8, 1)]
col_2 <- col_palette[sample.int(8, 1)]

ggplot() +
  geom_sf(data = container,
          color = NA,
          fill = col_background) +
  geom_sf(data = df_points_1,
          aes(size = size,
              color = factor(color))) +
  geom_sf(data = df_points_2,
          aes(size =  size,
              color = factor(color))) + 
  scale_color_manual(values = c("1" = "black", "2" = col_1, "3" = col_2)) +
  scale_size(range = c(0.01, 0.05)) +
  theme_void() +
  theme(legend.position = "none")

ggsave(filename = "sandcasted-alacena.png", 
       width = 8, 
       height = 12, 
       units = "in")
```

```{r}
col_palette <- mex.brewer("Revolucion")[-c(5, 6)]
col_background <- mex.brewer("Revolucion")[c(5, 6)]
col_background <- col_background[sample.int(2, 1)]
col_1 <- col_palette[sample.int(8, 1)]
col_2 <- col_palette[sample.int(8, 1)]

ggplot() +
  geom_sf(data = container,
          color = NA,
          fill = col_background) +
  geom_sf(data = df_points_1,
          aes(size = size,
              color = factor(color))) +
  geom_sf(data = df_points_2,
          aes(size =  size,
              color = factor(color))) + 
  scale_color_manual(values = c("1" = "black", "2" = col_1, "3" = col_2)) +
  scale_size(range = c(0.01, 0.05)) +
  theme_void() +
  theme(legend.position = "none")

ggsave(filename = "sandcasted-revolucion.png", 
       width = 8, 
       height = 12, 
       units = "in")
```
